### 2021-07-07 paper.tex
Initial commit

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{(Animal) Life-Cycle Algorithm\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.
This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax. This is a distributed algorithm in all its conception, where the idea is that its mechanism can operate from different containers (or equipment) independently, eliminating waiting times between processes. This algorithm emphasizes the use of cloud computing available resources.

Its mechanism is composed of birth, growth, reproduction, and death, where each one of them works concurrently and asynchronously on a population that evolves constantly. This strategy takes a similar focus as the study of bacteria growth in microbiology, where using a microscope, we can observe and analyze the evolution of a population over time.

This implementation also can be useful, as an introductory example to the native cloud computing programming, inspired by the GA algorithm operation mechanics. One difference from the GA is in the reproduction mechanism, which is flexible to work in parallel with several strategies simultaneously, for example, tourney selection, random selection of couples in the population, and couple selection with a random mating individual outside of the population.
\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{First Section}
\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{bibliografia}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

### 2021-07-09 paper.tex
Bibliography
Bib external file
Update paper.tex

@@
 %The abstract should briefly summarize the contents of the paper in 150--250 words.
-This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax.
-This is a distributed algorithm in all its conception, where the idea is that its mechanism can operate from different containers (or equipment) independently, eliminating waiting times between processes.
-This algorithm emphasizes the use of cloud computing available resources.
+There are several bio-inspired algorithms that are use analogies of na
 
-Its mechanism is composed of birth, growth, reproduction, and death, where each one of them works concurrently and asynchronously on a population that evolves constantly.
-This strategy takes a similar focus as the study of bacteria growth in microbiology, where using a microscope, we can observe and analyze the evolution of a population over time.
+This paper is a proposal for a novel nature-inspired algorithm that seeks to solve the
+basic GA problem OneMax. This is a distributed algorithm in all its conception,
 
-This implementation also can be useful, as an introductory example to the native cloud computing programming, inspired by the GA algorithm operation mechanics.
-One difference from the GA is in the reproduction mechanism, which is flexible to work in parallel with several strategies simultaneously, for example, tourney selection, random selection of couples in the population, and couple selection with a random mating individual outside of the population.
+% In this paper, we present a novel distributed nature-inspired algorithm, for solving 
+% optimization problems.
+
+% Considera la opción de arriba para el inicio, creo que es más concisa. 
+% El algoritmo es para problemas de optimización en general, no solo OneMax 
+% - Mario
+
+where the idea is that its mechanism can operate from different containers (or
+equipment) independently, eliminating waiting times between processes. This
+algorithm emphasizes the use of cloud computing available resources.
+
+% Algo como: from the ground up, the algorithm is designed as a cloud-native
+%
+
+% The algorithm in inspired in the biologycal life-cycle of animal species, which consists
+% of several phases  birth, growth, reproduction, and death. 
+% As in nature, we intend to execute all these "phases" in parallel and asynchronously
+
+Its mechanism is composed of birth, growth, reproduction, and death, where each
+one of them works concurrently and asynchronously on a population that evolves
+constantly. This strategy takes a similar focus as the study of bacteria growth
+in microbiology, where using a microscope, we can observe and analyze the
+evolution of a population over time.
+
+% As a proof-of-concept we implemented the algorithm  ... 
+% by using the OneMax problem  
+%
+
+This implementation also can be useful, as an introductory example to the native
+cloud computing programming, inspired by the GA algorithm operation mechanics.
+One difference from the GA is in the reproduction mechanism, which is flexible
+to work in parallel with several strategies simultaneously, for example, tournament 
+selection, random selection of couples in the population, and couple selection
+with a random mating individual outside of the population.
+
 \keywords{First keyword  \and Second keyword \and Another keyword.}

### 2021-07-15 paper.tex
some minor fixes

--- 2021-07-07 paper.tex
@@
 \documentclass[runningheads]{llncs}
+%
 %
@@
 %
-\title{(Animal) Life-Cycle Algorithm\thanks{Supported by organization x.}}
+\title{(Biological) Life-Cycle Algorithm\thanks{Supported by organization x.}}
 %
@@
 %The abstract should briefly summarize the contents of the paper in 150--250 words.
-This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax.
+
+% ----------------------------------
+% [History Drafts]
+% [Draft 1] This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax.
 This is a distributed algorithm in all its conception, where the idea is that its mechanism can operate from different containers (or equipment) independently, eliminating waiting times between processes.
 This algorithm emphasizes the use of cloud computing available resources.
-
 Its mechanism is composed of birth, growth, reproduction, and death, where each one of them works concurrently and asynchronously on a population that evolves constantly.
 This strategy takes a similar focus as the study of bacteria growth in microbiology, where using a microscope, we can observe and analyze the evolution of a population over time.
-
 This implementation also can be useful, as an introductory example to the native cloud computing programming, inspired by the GA algorithm operation mechanics.
 One difference from the GA is in the reproduction mechanism, which is flexible to work in parallel with several strategies simultaneously, for example, tourney selection, random selection of couples in the population, and couple selection with a random mating individual outside of the population.
+% ----------------------------------
+
+Several bio-inspired algorithms use population evolution as analogies of
+nature. In this paper, we followed a strategy that takes a similar approach as
+the study of bacteria growth in microbiology, where using a microscope, we can
+observe and analyze the evolution of a population over time. We present an
+algorithm inspired by the biological life-cycle of animal species, which
+consists of several stages: birth, growth, reproduction, and death. As in
+nature, we intend to execute all these stages in parallel and asynchronously on
+a population that evolves constantly. In this paper, we present a novel distributed nature-inspired algorithm for
+solving optimization problems. From the ground up, we designed the algorithm as
+a cloud-native solution using the cloud available resources to divide the
+processing workload, among several computers or running the algorithm as a
+cloud service. The algorithm works concurrently and asynchronously on a
+constantly evolving population, using different computers (or containers)
+independently, eliminating waiting times between processes. This algorithm 
+seeks to imitate the natural life cycle, where new individuals
+are born at any moment and mature over time, where they age and suffer
+mutations throughout their lives. In reproduction, couples match by mutual
+attraction, where they may have offspring. Death can happen to everyone: from a
+newborn to an aged adult, where the individual's fitness will impact their
+longevity. As a proof-of-concept, we implemented the algorithm with Docker
+containers by solving the OneMax problem comparing it with a basic (sequential) GA 
+algorithm, where it showed favorable and promising results.
+
 \keywords{First keyword  \and Second keyword \and Another keyword.}
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{bibliografia}
+\bibliographystyle{splncs04}
+\bibliography{bib/bibliografia.bib}
 %
-\begin{thebibliography}{8}
-\bibitem{ref_article1}
-Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-\bibitem{ref_lncs1}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\bibitem{ref_book1}
-Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-Location (1999)
-
-\bibitem{ref_proc1}
-Author, A.-B.: Contribution title. In: 9th International Proceedings
-on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-\bibitem{ref_url1}
-LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-Oct 2017
-\end{thebibliography}
 \end{document}

### 2021-07-15 history/paper_v2.tex
Abstract update
Work in progress.

--- 2021-07-15 paper.tex
@@
 nature, we intend to execute all these stages in parallel and asynchronously on
-a population that evolves constantly. In this paper, we present a novel distributed nature-inspired algorithm for
+a population that evolves constantly.
+
+In this paper, we present a novel distributed nature-inspired algorithm for
 solving optimization problems. From the ground up, we designed the algorithm as
 a cloud-native solution using the cloud available resources to divide the
-processing workload, among several computers or running the algorithm as a
+processing work-load, among several computers or running the algorithm as a
 cloud service. The algorithm works concurrently and asynchronously on a
 constantly evolving population, using different computers (or containers)
-independently, eliminating waiting times between processes. This algorithm 
-seeks to imitate the natural life cycle, where new individuals
+independently, eliminating waiting times between processes.
+
+This algorithm seeks to imitate the natural life cycle, where new individuals
 are born at any moment and mature over time, where they age and suffer
@@
 longevity. As a proof-of-concept, we implemented the algorithm with Docker
-containers by solving the OneMax problem comparing it with a basic (sequential) GA 
-algorithm, where it showed favorable and promising results.
+containers by solving the OneMax problem comparing it with a basic GA
+(sequential) algorithm, where it showed favorable and promising results.
 

### 2021-07-15 paper.tex
Abstarct updated
Line spaces.

@@
 %
-\title{(Biological) Life-Cycle Algorithm\thanks{Supported by organization x.}}
+\title{A novel distributed nature-inspired algorithm for solving optimization problems (Life-Cycle Algorithm)\thanks{Supported by organization x.}}
 %
@@
 
-% ----------------------------------
-% [History Drafts]
-% [Draft 1] This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax.
-This is a distributed algorithm in all its conception, where the idea is that its mechanism can operate from different containers (or equipment) independently, eliminating waiting times between processes.
-This algorithm emphasizes the use of cloud computing available resources.
-Its mechanism is composed of birth, growth, reproduction, and death, where each one of them works concurrently and asynchronously on a population that evolves constantly.
-This strategy takes a similar focus as the study of bacteria growth in microbiology, where using a microscope, we can observe and analyze the evolution of a population over time.
-This implementation also can be useful, as an introductory example to the native cloud computing programming, inspired by the GA algorithm operation mechanics.
-One difference from the GA is in the reproduction mechanism, which is flexible to work in parallel with several strategies simultaneously, for example, tourney selection, random selection of couples in the population, and couple selection with a random mating individual outside of the population.
-% ----------------------------------
-
 Several bio-inspired algorithms use population evolution as analogies of
-nature. In this paper, we followed a strategy that takes a similar approach as
-the study of bacteria growth in microbiology, where using a microscope, we can
-observe and analyze the evolution of a population over time. We present an
-algorithm inspired by the biological life-cycle of animal species, which
-consists of several stages: birth, growth, reproduction, and death. As in
-nature, we intend to execute all these stages in parallel and asynchronously on
-a population that evolves constantly. In this paper, we present a novel distributed nature-inspired algorithm for
-solving optimization problems. From the ground up, we designed the algorithm as
-a cloud-native solution using the cloud available resources to divide the
-processing workload, among several computers or running the algorithm as a
-cloud service. The algorithm works concurrently and asynchronously on a
-constantly evolving population, using different computers (or containers)
-independently, eliminating waiting times between processes. This algorithm 
-seeks to imitate the natural life cycle, where new individuals
-are born at any moment and mature over time, where they age and suffer
-mutations throughout their lives. In reproduction, couples match by mutual
-attraction, where they may have offspring. Death can happen to everyone: from a
-newborn to an aged adult, where the individual's fitness will impact their
-longevity. As a proof-of-concept, we implemented the algorithm with Docker
-containers by solving the OneMax problem comparing it with a basic (sequential) GA 
-algorithm, where it showed favorable and promising results.
+nature. In this paper, we present an algorithm inspired by the biological
+life-cycle of animal species, which consists of several stages: birth, growth,
+reproduction, and death. As in nature, we intend to execute all these stages in
+parallel and asynchronously on a population that evolves constantly. From the
+ground up, we designed the algorithm as a cloud-native solution using the cloud
+available resources to divide the processing workload, among several computers
+or running the algorithm as a cloud service. The algorithm works concurrently
+and asynchronously on a constantly evolving population, using different
+computers (or containers) independently, eliminating waiting times between
+processes. This algorithm seeks to imitate the natural life cycle, where new
+individuals are born at any moment and mature over time, where they age and
+suffer mutations throughout their lives. In reproduction, couples match by
+mutual attraction, where they may have offspring. Death can happen to everyone:
+from a newborn to an aged adult, where the individual's fitness will impact
+their longevity. As a proof-of-concept, we implemented the algorithm with
+Docker containers by solving the OneMax problem comparing it with a basic
+(sequential) GA algorithm, where it showed favorable and promising results.
 

### 2021-08-16 paper.tex
update
Title Update
Work in progress.
First draft
This is a work in progress, needs improvement.

@@
 %
-\title{A novel distributed nature-inspired algorithm for solving optimization problems (Life-Cycle Algorithm)\thanks{Supported by organization x.}}
+\title{A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}}
+% (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
 %
@@
 \end{abstract}
+
+\section{Introduction}
+
+Bio-inspired algorithms have been very successful when
+used to solve complex optimization problems, but as their complexity increases
+so does the computing power required. One strategy to address this processing
+need is to use distributed computing, or the resources available in the cloud
+to help find the solution. This strategy gives us elasticity to increase (or
+reduce) the computing power to achieve a balance according to the nature of the
+problem.
+
+One of the problems that we have identified in this research is that most
+bio-inspired algorithms are designed with a traditionally sequential
+perspective, where each process must wait for the previous task to finish
+before continuing. Some architectures address this issue, what distinguishes
+us, is that our proposal presents an algorithm designed in its entirety as a
+native solution in the cloud, fully distributed, where its processes are
+executed in parallel and asynchronously. This technique makes it easy to scale
+the computing power according to the complexity required by the problem.
+
+We designed our algorithm using observation, analysis, and abstraction in
+nature to identify what most species in the animal kingdom have in common,
+where individuals of a population that best adapt to the environment have
+greater chances of survival, reproduction, and improvement of the species.
+Imagining as if the task of writing these rules of evolution was in our hands,
+questioning how we could solve it?
+
+Similar to nature, we identified what most species have in common in the life
+cycle. Our algorithm works on a constantly evolving population, experiencing
+the stages that all living beings undergo: being born, growing up, reproducing,
+and dying, where each of these stages will be processes (of our algorithm) that
+randomly affect the population individuals, emulating the organic way.
+
+This algorithm seeks to imitate the natural life cycle, where new individuals
+are born at any moment and mature over time, where they age and suffer
+mutations throughout their lives. In reproduction, couples match by mutual
+attraction, where they may have offspring. Death can happen to everyone: from a
+newborn to an aged adult, where the individual's fitness will impact their
+longevity.
+
+In this research, we seek to demonstrate that it is possible to evolve a
+population of individuals, similar to a Genetic Algorithm (GA), using a
+distributed, parallel, and asynchronous methodology.
+
+\section{Description of the sections of the Paper}
+
+\section{State of the art}
+
+One of the publications with the most influence and impact on our research,
+which inspired us to carry out this project is "A container-based cloud-native
+architecture for the reproducible execution of multi-population optimization
+algorithms" by Mario García Valdez and Juan J. Merelo Guervós.
+
+They propose a cloud-native optimization framework, that can include multiple
+(population-based) algorithms without increasing the number of parameters that
+need tuning. Their solution can support different algorithms at the same time,
+work asynchronously, and also be readily deployable to any cloud platform.
+
+"Splitting a population into multiple instances is a technique used extensively
+in recent years to help improve the performance of nature-inspired optimization
+algorithms. Work on those populations can be done in parallel, and they can
+interact asynchronously, a fact that can be leveraged to create scalable
+implementations based on, among other methods, distributed, multi-threaded,
+parallel, and cloud-native computing". [All of the above taken from their publication]
+
+[Note: This draft is a work in progress, needs improvement]
+
+\section{Proposal}
+
+From the ground up, we designed the algorithm as a cloud-native solution using
+the cloud available resources to divide the processing workload, among several
+computers or running the algorithm as a cloud service. The algorithm works
+concurrently and asynchronously on a constantly evolving population, using
+different computers (or containers) independently, eliminating waiting times
+between processes.
+
+In this paper, we present an algorithm inspired by the biological life-cycle of
+animal species, which consists of several stages: birth, growth, reproduction,
+and death. As in nature, we intend to execute all these stages in parallel and
+asynchronously on a population that evolves constantly. This algorithm starts
+with a randomly generated population, where the processes will interact with
+the population independently. This means that at any given time, any individual
+can experience any of these processes.
+
+\subsection{Birth}
+
+Similar to a GA, our algorithm starts with the process responsible for the
+random generation of individuals. In our scheme, we call it birth, however, we
+must mention that the successful reproduction process will result in the birth
+of new individuals (offspring).
+
+\subsection{Growth}
+
+As in nature, all individuals constantly grow, mature, or age. With increasing
+age, individuals may lose strength but also gain more knowledge to solve
+problems. We represent this with a possible mutation in each increment of age.
+The growth process will take an individual to assess whether it's ready to
+mature and undergo changes.
+
+\subsection{Reproduction}
+
+The attraction of a couple will depend on fitness: the better individual's
+fitness, the more attractive it will be, making it easier to find mating
+matches. Not all couples will be compatible, so reproduction will not always be
+possible, but the problem arises: how to quantify the attraction between two
+individuals?. The reproduction process will be taking random pairs of
+individuals to evaluate their attraction as a couple, to try to breed; when the
+gestation is successful, a new pair of individuals will be born (as the
+offspring).
+
+\subsection{Death}
+
+The process of dying represents the challenges and adversities that life
+presents (to overcome). This process evaluates the individual resistance to
+survive in the environment. The better fitness the individual has will increase
+its chances of survival. As time progresses, the demands of nature will also
+increase, pushing for only the best individuals to survive.
+
+\section{Experimental}
+
+As a proof-of-concept, we implemented the algorithm with Docker containers by
+solving the OneMax problem comparing it with a basic (sequential) GA algorithm,
+where it showed favorable and promising results.
+
 %
@@
 %
-\section{First Section}
+
+% Introducción 
+% Contexto: Los algoritmos bioinsirados se utilzan para resolver 
+% problemas complejos, pero en ocasiones se requiere de poder
+% computo.
+% Problemas: La mayoría de los algoritmos bio inspiarados
+% no están diseñandos con perspectiva distribuida, paralela y asíncrona. 
+% De que hay arquitecturas que tratan esta problematica. 
+% Propuesta. 
+% Descripción de las secciones del paper.
+
+% Estado del Arte 
+% PSO distribuido, GAs, etc.
+
+% Propuesta
+%
+
+% Experimental 
+% Setup 
+% OneMax
+% Results
+
+% Conclusiones
+
+\section{Another Section}
 \subsection{A Subsection Sample}

### 2021-08-16 paper.tex
Paper update
Work in progress

@@
 As a proof-of-concept, we implemented the algorithm with Docker containers by
-solving the OneMax problem comparing it with a basic (sequential) GA algorithm,
-where it showed favorable and promising results.
+solving the OneMax problem to compare it with a traditional (sequential) GA
+algorithm using the DEAP library. The OneMax problem uses a genetic algorithm
+to evolve a population of randomly generated individuals with zeros and ones,
+and it stops until a solution of only ones is found.
+
+In this experiment, we needed to match or balance the experimentation
+parameters according to the specifications of the algorithm used by the DEAP
+library. This is to be able to verify if our algorithm would also converge on
+the solutions in a similar number of evaluations and execution time.
+
+\section{Results}
+
+In our experiments, we found that for simple problems, the cost of
+communication between containers will increase the total time of execution,
+however, we believe that the opposite must also be true: for complex problems,
+distributing the work on multiple resources must reduce time, making the
+communication cost negligible.
+
+This scheme allows for multiple parameter's fine tunning, granting us the
+freedom to experiment with different selection and reproduction strategies
+simultaneously, which will impact how fast it finds the solution and the
+obtained quality.
+
+\section{Conclusions}
+
+In this research, we were able to demonstrate that it is possible to evolve a
+population of individuals, similar to a Genetic Algorithm (GA), using a
+distributed, parallel, and asynchronous methodology.
+
+We implemented the algorithm with Docker containers by solving the OneMax
+problem comparing it with a traditional (sequential) GA algorithm, where it
+showed favorable and promising results. To further validate this work we could
+use control or something more complex and demanding problem that requires to
+compute real numbers.
 

### 2021-09-02 paper.tex
Draft update
Work in progress
Draft Update
Paper updated to be as close as possible to the presentation.

@@
 
-Bio-inspired algorithms have been very successful when
-used to solve complex optimization problems, but as their complexity increases
-so does the computing power required. One strategy to address this processing
-need is to use distributed computing, or the resources available in the cloud
-to help find the solution. This strategy gives us elasticity to increase (or
-reduce) the computing power to achieve a balance according to the nature of the
-problem.
+Bio-inspired algorithms have been very successful when used to solve complex
+optimization problems, but as their complexity increases so does the computing
+power required. One strategy to address this processing need is to use
+distributed computing, or the resources available in the cloud to help find the
+solution. This strategy gives us elasticity to increase (or reduce) the
+computing power to achieve a balance according to the nature of the problem.
 
@@
 
-One of the publications with the most influence and impact on our research,
-which inspired us to carry out this project is "A container-based cloud-native
-architecture for the reproducible execution of multi-population optimization
-algorithms" by Mario García Valdez and Juan J. Merelo Guervós.
+\subsection{Background}
 
-They propose a cloud-native optimization framework, that can include multiple
-(population-based) algorithms without increasing the number of parameters that
-need tuning. Their solution can support different algorithms at the same time,
-work asynchronously, and also be readily deployable to any cloud platform.
+One of the publications with the most influence on our research proposes a
+cloud-native optimization framework, that can include multiple
+(population-based) algorithms [1]. In their research, they work with ideas such
+as:
 
-"Splitting a population into multiple instances is a technique used extensively
-in recent years to help improve the performance of nature-inspired optimization
-algorithms. Work on those populations can be done in parallel, and they can
-interact asynchronously, a fact that can be leveraged to create scalable
-implementations based on, among other methods, distributed, multi-threaded,
-parallel, and cloud-native computing". [All of the above taken from their publication]
-
-[Note: This draft is a work in progress, needs improvement]
+These ideas planted the seed of thought in our current presentation.
 
@@
 the cloud available resources to divide the processing workload, among several
-computers or running the algorithm as a cloud service. The algorithm works
+computers or running the algorithm as a cloud service. [The algorithm works
 concurrently and asynchronously on a constantly evolving population, using
 different computers (or containers) independently, eliminating waiting times
-between processes.
+between processes.]
 
@@
 and death. As in nature, we intend to execute all these stages in parallel and
-asynchronously on a population that evolves constantly. This algorithm starts
-with a randomly generated population, where the processes will interact with
-the population independently. This means that at any given time, any individual
-can experience any of these processes.
+asynchronously on a population that evolves constantly.
+
+This algorithm seeks to imitate the natural life cycle, where new individuals
+are born at any moment and mature over time, where they age and suffer
+mutations throughout their lives. In reproduction, couples match by mutual
+attraction, where they may have offspring. Death can happen to everyone: from a
+newborn to an aged adult, where the individual's fitness will impact their
+longevity.
 
@@
 
-Similar to a GA, our algorithm starts with the process responsible for the
-random generation of individuals. In our scheme, we call it birth, however, we
-must mention that the successful reproduction process will result in the birth
-of new individuals (offspring).
+This algorithm starts with a randomly generated population, where the processes
+will interact with the population independently. This means that at any given
+time, any individual can experience any of these processes. Birth is the first
+process of our algorithm, and it is responsible for the initial generation of
+individuals.
 
@@
 possible, but the problem arises: how to quantify the attraction between two
-individuals?. The reproduction process will be taking random pairs of
-individuals to evaluate their attraction as a couple, to try to breed; when the
-gestation is successful, a new pair of individuals will be born (as the
-offspring).
+individuals?. This process will be taking random pairs of individuals to
+evaluate their attraction as a couple, to try to breed; when the gestation is
+successful, a new pair of individuals will be born (as the offspring).
 
@@
 
-The process of dying represents the challenges and adversities that life
-presents (to overcome). This process evaluates the individual resistance to
-survive in the environment. The better fitness the individual has will increase
-its chances of survival. As time progresses, the demands of nature will also
+The death stage represents the challenges and adversities that life presents
+(to overcome). This process evaluates the individual resistance to survive in
+the environment. The better fitness the individual has will increase its
+chances of survival. As time progresses, the demands of nature will also
 increase, pushing for only the best individuals to survive.
 
-\section{Experimental}
+\section{Experiments}
 
@@
 
-\section{Results}
+\subsection{Experimental Setup}
+
+\subsection{Results}
+
+\section{Discussion}
 
@@
 
-In this research, we were able to demonstrate that it is possible to evolve a
-population of individuals, similar to a Genetic Algorithm (GA), using a
-distributed, parallel, and asynchronous methodology.
-
 We implemented the algorithm with Docker containers by solving the OneMax
 problem comparing it with a traditional (sequential) GA algorithm, where it
-showed favorable and promising results. To further validate this work we could
-use control or something more complex and demanding problem that requires to
-compute real numbers.
+showed favorable and promising results. To further validate this work, we could
+use control or some more complex and demanding problem that requires computing
+real numbers.
+
+As the complexity of problems increases, it is essential to have a scalable,
+replicable, and fault-tolerant model that uses collaborative techniques to work
+in the cloud, where multiple resources will be communicating asynchronously.
+This research has shown that it is possible to evolve a population of
+individuals, similar to a Genetic Algorithm (GA), using a distributed,
+parallel, and asynchronous methodology.
 

### 2021-09-02 paper.tex
Tables Update
Experiment Config & Result Tables

@@
 
+    \begin{table}[]
+        \begin{tabular}{|l|l|}
+        \hline
+        \multicolumn{2}{|l|}{OneMax   (DEAP)} \\ \hline
+        Population & 60 \\ \hline
+        Max   Generation & 20 \\ \hline
+        Stagnation & Off \\ \hline
+        Chromosome   Length & 20 \\ \hline
+        Target   Fitness & 20 \\ \hline
+        Crossover   Rate & 100 \\ \hline
+        Mutation   Rate & 7 \\ \hline
+        Tourney   Reprod. Rate & 50 \\ \hline
+        Tourney   Sample & 3 \\ \hline
+        \end{tabular}
+        \end{table}
+
+    \begin{table}[]
+        \begin{tabular}{|l|l|}
+        \hline
+        \multicolumn{2}{|l|}{LifeCycle   Algorithm} \\ \hline
+        Population & 60 \\ \hline
+        Max   Generation & 20 \\ \hline
+        Stagnation & Off \\ \hline
+        Chromosome   Length & 20 \\ \hline
+        Target   Fitness & 20 \\ \hline
+        Crossover   Rate & 100 \\ \hline
+        Mutation   Rate & 7 \\ \hline
+        Tourney   Reprod. Rate & 50 \\ \hline
+        Tourney   Sample & 4 \\ \hline
+        Max   Age & 80 \\ \hline
+        Open   Reprod. Rate & 5 \\ \hline
+        Closed   Reprod. Rate & 45 \\ \hline
+        Fertility   Rate & 100 \\ \hline
+        Base   Approval & 80 \\ \hline
+        Goal   Approval & 100 \\ \hline
+        Max   Wait Time & 2 \\ \hline
+        \end{tabular}
+        \end{table}
+
 \subsection{Results}
+
+    \begin{table}[]
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+        \multicolumn{5}{|c|}{\textbf{OneMax DEAP}} \\ \hline
+        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
+        1 & 6 & 20 & 360 & 0.016 \\ \hline
+        2 & 5 & 20 & 300 & 0.032 \\ \hline
+        3 & 7 & 20 & 420 & 0.061 \\ \hline
+        4 & 9 & 20 & 540 & 0.081 \\ \hline
+        5 & 8 & 20 & 480 & 0.080 \\ \hline
+        6 & 6 & 20 & 360 & 0.062 \\ \hline
+        7 & 7 & 20 & 420 & 0.062 \\ \hline
+        8 & 6 & 20 & 360 & 0.016 \\ \hline
+        9 & 8 & 20 & 480 & 0.058 \\ \hline
+        10 & 6 & 20 & 360 & 0.050 \\ \hline
+        11 & 7 & 20 & 420 & 0.073 \\ \hline
+        12 & 8 & 20 & 480 & 0.076 \\ \hline
+        13 & 8 & 20 & 480 & 0.065 \\ \hline
+        14 & 6 & 20 & 360 & 0.060 \\ \hline
+        15 & 6 & 20 & 360 & 0.045 \\ \hline
+        16 & 6 & 20 & 360 & 0.059 \\ \hline
+        17 & 6 & 20 & 360 & 0.061 \\ \hline
+        18 & 6 & 20 & 360 & 0.058 \\ \hline
+        19 & 5 & 20 & 300 & 0.060 \\ \hline
+        20 & 7 & 20 & 420 & 0.067 \\ \hline
+        21 & 7 & 20 & 420 & 0.060 \\ \hline
+        22 & 7 & 20 & 420 & 0.085 \\ \hline
+        23 & 7 & 20 & 420 & 0.071 \\ \hline
+        24 & 4 & 20 & 300 & 0.049 \\ \hline
+        25 & 6 & 20 & 360 & 0.050 \\ \hline
+        26 & 9 & 20 & 540 & 0.081 \\ \hline
+        27 & 6 & 20 & 420 & 0.074 \\ \hline
+        28 & 6 & 20 & 360 & 0.064 \\ \hline
+        29 & 6 & 20 & 360 & 0.065 \\ \hline
+        30 & 4 & 20 & 240 & 0.016 \\ \hline
+        Avg. & 6.5 & 20 & 394 & 0.059 \\ \hline
+        \end{tabular}
+        \end{table}
+
+    \begin{table}[]
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+        \multicolumn{5}{|c|}{\textbf{LifeCycle Algorithm}} \\ \hline
+        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
+        1 & 8 & 20 & 486 & 6.65 \\ \hline
+        2 & 6 & 20 & 381 & 5.20 \\ \hline
+        3 & 6 & 20 & 369 & 5.69 \\ \hline
+        4 & 7 & 20 & 434 & 6.37 \\ \hline
+        5 & 12 & 20 & 731 & 8.20 \\ \hline
+        6 & 5 & 20 & 306 & 4.55 \\ \hline
+        7 & 13 & 20 & 764 & 8.34 \\ \hline
+        8 & 4 & 20 & 233 & 4.09 \\ \hline
+        9 & 12 & 20 & 692 & 7.27 \\ \hline
+        10 & 6 & 20 & 338 & 4.76 \\ \hline
+        11 & 9 & 20 & 559 & 7.78 \\ \hline
+        12 & 12 & 20 & 730 & 8.35 \\ \hline
+        13 & 4 & 20 & 219 & 3.43 \\ \hline
+        14 & 8 & 20 & 462 & 5.28 \\ \hline
+        15 & 4 & 20 & 217 & 3.37 \\ \hline
+        16 & 4 & 20 & 234 & 4.54 \\ \hline
+        17 & 4 & 20 & 256 & 4.35 \\ \hline
+        18 & 12 & 20 & 714 & 8.14 \\ \hline
+        19 & 12 & 20 & 694 & 7.88 \\ \hline
+        20 & 15 & 20 & 892 & 9.74 \\ \hline
+        21 & 11 & 20 & 633 & 7.98 \\ \hline
+        22 & 3 & 20 & 169 & 4.02 \\ \hline
+        23 & 10 & 20 & 611 & 6.89 \\ \hline
+        24 & 10 & 20 & 629 & 7.32 \\ \hline
+        25 & 7 & 20 & 416 & 6.22 \\ \hline
+        26 & 7 & 20 & 446 & 5.55 \\ \hline
+        27 & 6 & 20 & 379 & 5.95 \\ \hline
+        28 & 8 & 20 & 466 & 6.98 \\ \hline
+        29 & 3 & 20 & 197 & 3.36 \\ \hline
+        30 & 6 & 20 & 381 & 6.16 \\ \hline
+        Avg. & 7.8 & 20 & 468 & 6.15 \\ \hline
+        \end{tabular}
+        \end{table}
 
@@
 % Conclusiones
+
+\section{Ignored Elements}
 
@@
 \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+
 %

### 2021-09-02 paper.tex
Tables Update
Work in progress.

@@
 \subsection{Experimental Setup}
+    Table~\ref{tab1} shows the configuration for the OneMax DEAP version, while Table~\ref{tab2} shows the LifeCycle Algorithm setup.
 
     \begin{table}[]
+        \centering
+        \caption{OneMax DEAP configuration.}\label{tab1}
         \begin{tabular}{|l|l|}
@@
     \begin{table}[]
+        \centering        
+        \caption{LifeCycle Algorithm configuration.}\label{tab2}
         \begin{tabular}{|l|l|}
@@
 \subsection{Results}
+    Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.
 
     \begin{table}[]
+        \centering        
+        \caption{OneMax DEAP experiment results.}\label{tab3}        
         \begin{tabular}{|l|l|l|l|l|}
@@
     \begin{table}[]
+        \centering        
+        \caption{LifeCycle Algorithm experiment results.}\label{tab4}
         \begin{tabular}{|l|l|l|l|l|}
@@
 The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
+headings. Table~\ref{tab5} gives a summary of all heading levels.
 
@@
 \caption{Table captions should be placed above the
-tables.}\label{tab1}
+tables.}\label{tab5}
 \begin{tabular}{|l|l|l|}

### 2021-09-02 paper.tex
Figures Update
New figures added to paper.

@@
 %
-%\titlerunning{Abbreviated paper title}
+\titlerunning{Life-Cycle Algorithm}
 % If the paper title is too long for the running head, you can set
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{J. C. Felix-Saul \inst{1} \and
+Mario García Valdez\inst{1} \and
+Juan J. Merelo Guervós\inst{2}}
 %
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
+\institute{Department of Graduate Studies, Tijuana Institute of Technology, Tijuana, Mexico \and
+Department of Computer Architecture and Technology, Universidad de Granada, Granada, Spain}
 %
@@
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Distributed Bioinspired Algorithms  \and Genetic Algorithms \and Cloud Computing.}
 \end{abstract}
@@
 (population-based) algorithms [1]. In their research, they work with ideas such
-as:
+as those mentioned in Fig.~\ref{fig1}.
 
-These ideas planted the seed of thought in our current presentation.
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig1_background.pdf}
+    \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
+    \end{figure}
 
@@
 and death. As in nature, we intend to execute all these stages in parallel and
-asynchronously on a population that evolves constantly.
+asynchronously on a population that evolves constantly. We show the LifeCycle 
+Algorithm Proposal Model in Fig.~\ref{fig2}.
 
@@
 longevity.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig2_proposal.pdf}
+    \caption{LifeCycle Algorithm Proposal Model.} \label{fig2}
+    \end{figure}
 
@@
 schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
+Fig.~\ref{fig9}).
 
@@
 Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
+justified by the macro package automatically.} \label{fig9}
 \end{figure}

### 2021-09-02 paper.tex
References Update
Work in progress

@@
 
+Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.
+
+% For citations of references, we prefer the use of square brackets
+% and consecutive numbers. Citations using labels or the author/year
+% convention are also acceptable. The following bibliography provides
+% a sample reference list with entries for journal
+% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
+% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
+% and a homepage~\cite{ref_url1}. Multiple citations are grouped
+% \cite{ref_article1,ref_lncs1,ref_book1},
+% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+
 \subsection{Background}
@@
 cloud-native optimization framework, that can include multiple
-(population-based) algorithms [1]. In their research, they work with ideas such
+(population-based) algorithms~\cite{valdez2021container}. In their research, they work with ideas such
 as those mentioned in Fig.~\ref{fig1}.
@@
 
-\section{Ignored Elements}
-
-\section{Another Section}
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
-
-Subsequent paragraphs, however, are indented.
-
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
-
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab5} gives a summary of all heading levels.
-
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab5}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
-
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig9}).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig9}
-\end{figure}
-
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-
 %

### 2021-09-28 paper.tex
Draft Update
Supported Organization Update
Work in progress
Working on the experiment results.

@@
 %
-\title{A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}}
+\title{A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}}
 % (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
@@
 Several bio-inspired algorithms use population evolution as analogies of
-nature. In this paper, we present an algorithm inspired by the biological
-life-cycle of animal species, which consists of several stages: birth, growth,
-reproduction, and death. As in nature, we intend to execute all these stages in
-parallel and asynchronously on a population that evolves constantly. From the
-ground up, we designed the algorithm as a cloud-native solution using the cloud
-available resources to divide the processing workload, among several computers
-or running the algorithm as a cloud service. The algorithm works concurrently
-and asynchronously on a constantly evolving population, using different
-computers (or containers) independently, eliminating waiting times between
-processes. This algorithm seeks to imitate the natural life cycle, where new
-individuals are born at any moment and mature over time, where they age and
-suffer mutations throughout their lives. In reproduction, couples match by
-mutual attraction, where they may have offspring. Death can happen to everyone:
-from a newborn to an aged adult, where the individual's fitness will impact
-their longevity. As a proof-of-concept, we implemented the algorithm with
-Docker containers by solving the OneMax problem comparing it with a basic
-(sequential) GA algorithm, where it showed favorable and promising results.
+na-ture. In this paper, we present an algorithm inspired by the biological
+Life-Cycle of animal species, which consists of several stages: birth, growth,
+re-production, and death. As in nature, we intend to execute all these stages
+in parallel and asynchronously on a population that evolves constantly. From
+the ground up, we designed the algorithm as a cloud-native solution using the
+cloud available resources to divide the processing workload, among several
+computers or running the algorithm as a cloud service. The algorithm works
+concurrently and asynchronously on a constantly evolving population, using
+different computers (or containers) independently, eliminating waiting times
+between processes. This algorithm seeks to imitate the natural life cycle,
+where new individuals are born at any moment and mature over time, where they
+age and suffer mutations throughout their lives. In reproduction, couples match
+by mutual attraction, where they may have offspring. Death can happen to
+everyone: from a newborn to an aged adult, where the individual's fitness will
+impact their longevity. As a proof-of-concept, we implemented the algo-rithm
+with Docker containers by solving the OneMax problem comparing it with a basic
+(sequential) GA algorithm, where it showed favorable and prom-ising results.
 
@@
 distributed computing, or the resources available in the cloud to help find the
-solution. This strategy gives us elasticity to increase (or reduce) the
+solution. This strategy gives us elasticity to adjust (increase or reduce) the
 computing power to achieve a balance according to the nature of the problem.
@@
 
-Similar to nature, we identified what most species have in common in the life
-cycle. Our algorithm works on a constantly evolving population, experiencing
-the stages that all living beings undergo: being born, growing up, reproducing,
-and dying, where each of these stages will be processes (of our algorithm) that
+Like nature, we identified what most species have in common in the life cycle.
+Our algorithm works on a constantly evolving population, experiencing the
+stages that all living beings undergo: being born, growing up, reproducing, and
+dying, where each of these stages will be processes (of our algorithm) that
 randomly affect the population individuals, emulating the organic way.
-
-This algorithm seeks to imitate the natural life cycle, where new individuals
-are born at any moment and mature over time, where they age and suffer
-mutations throughout their lives. In reproduction, couples match by mutual
-attraction, where they may have offspring. Death can happen to everyone: from a
-newborn to an aged adult, where the individual's fitness will impact their
-longevity.
 
@@
 
+In this paper, we present an algorithm inspired by the biological Life-Cycle of
+animal species, which consists of several stages: birth, growth, reproduction,
+and death. As in nature, we intend to execute all these stages in parallel and
+asynchronously on a population that evolves constantly.
+
 From the ground up, we designed the algorithm as a cloud-native solution using
 the cloud available resources to divide the processing workload, among several
-computers or running the algorithm as a cloud service. [The algorithm works
+computers or running the algorithm as a cloud service. The algorithm works
 concurrently and asynchronously on a constantly evolving population, using
-different computers (or containers) independently, eliminating waiting times
-between processes.]
-
-In this paper, we present an algorithm inspired by the biological life-cycle of
-animal species, which consists of several stages: birth, growth, reproduction,
-and death. As in nature, we intend to execute all these stages in parallel and
-asynchronously on a population that evolves constantly. We show the LifeCycle 
-Algorithm Proposal Model in Fig.~\ref{fig2}.
+different computers (or containers) independently, theoretically eliminating
+waiting times between processes.
 
@@
     \includegraphics[width=\textwidth]{img/fig2_proposal.pdf}
-    \caption{LifeCycle Algorithm Proposal Model.} \label{fig2}
+    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig2}
     \end{figure}
@@
 fitness, the more attractive it will be, making it easier to find mating
-matches. Not all couples will be compatible, so reproduction will not always be
-possible, but the problem arises: how to quantify the attraction between two
-individuals?. This process will be taking random pairs of individuals to
-evaluate their attraction as a couple, to try to breed; when the gestation is
-successful, a new pair of individuals will be born (as the offspring).
+matches. This process will be taking random pairs of individuals to evaluate
+their attraction as a couple, to try to breed; when the gestation is
+successful, a new pair of individuals will be born (as the offspring). Not all
+couples will be compatible, so reproduction will not always be possible, but
+the problem arises: how to quantify the attraction between two individuals?
+
+We could have used several strategies to evaluate this attraction. Considering
+this algorithm takes a similar focus as the study of bacteria growth in
+microbiology, where we can observe and analyze the evolution of a population
+over time. As in nature' most species, the bigger a specimen is, the more
+attractive it is to its mating candidates. To be consistent with both ideas in
+our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
+to calculate the attraction between two individuals, where we visualize the
+individual fitness as its mass when using the equation. In previous work,
+Newton's Law of Universal Gravitation has shown success in helping to solve
+optimization problems.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig3_newtonslaw.pdf}
+    \caption{Newton's Law of Universal Gravitation.} \label{fig3}
+    \end{figure}
+
+Where:
+•	F is the gravitational force acting between two objects
+•	m1 and m2 are the masses of the objects
+•	r is the distance between the centers of their masses
+•	G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2
 
@@
 
-The death stage represents the challenges and adversities that life presents
-(to overcome). This process evaluates the individual resistance to survive in
-the environment. The better fitness the individual has will increase its
-chances of survival. As time progresses, the demands of nature will also
-increase, pushing for only the best individuals to survive.
+The death stage represents the challenges and adversities that life presents to
+overcome. This process evaluates the individual resistance to survive in the
+environment. The better fitness the individual has will increase its chances of
+survival. As time progresses, the demands of nature will also increase, pushing
+for only the best individuals to survive.
+
+\subsection{Life-Cycle algorithm flowchart}
+
+The figure 4 describes the general flowchart for the Life-Cycle algorithm.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
+    \caption{Life-Cycle algorithm general flowchart.} \label{fig4}
+    \end{figure}
 
@@
 As a proof-of-concept, we implemented the algorithm with Docker containers by
-solving the OneMax problem to compare it with a traditional (sequential) GA
-algorithm using the DEAP library. The OneMax problem uses a genetic algorithm
-to evolve a population of randomly generated individuals with zeros and ones,
-and it stops until a solution of only ones is found.
+solving the OneMax problem to compare it with a traditional GA algorithm using
+the DEAP (Distributed Evolutionary Algorithms in Python) library. The OneMax
+problem uses a genetic algorithm to evolve a population of randomly generated
+individuals with zeros and ones, and it stops until a solution of only ones is
+found.
+
+\subsection{Experimental Setup}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig5_processes_containers .pdf}
+    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig5}
+    \end{figure}
+
+One strategic difference in our algorithm implementation is the reproduction
+process, which is flexible to work in parallel with multiple couple selection
+methods, for example, tournament selection, random selection (closed
+reproduction), and couple match by creating a new mating individual (open
+reproduction). We use many combinations of the containerized processes, up to
+the minimum number required to obtain good results. Figure 4 shows a comparison
+of only two alternatives for the implementation of the algorithm. Our
+experimentation started with a configuration of ten processes and ended in
+five, shown on the left and right sides of figure 4, respectively.
+
+\subsection{Experiment Configuration}
 
@@
 the solutions in a similar number of evaluations and execution time.
-
-\subsection{Experimental Setup}
-    Table~\ref{tab1} shows the configuration for the OneMax DEAP version, while Table~\ref{tab2} shows the LifeCycle Algorithm setup.
+Table~\ref{tab1} shows the OneMax initial configuration for DEAP and Life-Cycle
+experiment.
 
@@
     \centering        
-        \caption{OneMax DEAP configuration.}\label{tab1}
-        \begin{tabular}{|l|l|}
-        \hline
-        \multicolumn{2}{|l|}{OneMax   (DEAP)} \\ \hline
-        Population & 60 \\ \hline
-        Max   Generation & 20 \\ \hline
-        Stagnation & Off \\ \hline
-        Chromosome   Length & 20 \\ \hline
-        Target   Fitness & 20 \\ \hline
-        Crossover   Rate & 100 \\ \hline
-        Mutation   Rate & 7 \\ \hline
-        Tourney   Reprod. Rate & 50 \\ \hline
-        Tourney   Sample & 3 \\ \hline
+    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab1}
+    \begin{tabular}{lll}
+    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\
+    Population & 60 & 60 \\
+    Max Generation & 20 & 20 \\
+    Stagnation & Off & 10 \\
+    Chromosome Length & 20 & 20 \\
+    Target Fitness & 20 & 20 \\
+    Crossover Rate & 100 & 100 \\
+    Mutation Rate & 7 & 7 \\
+    Tournament Rate & 100 & 50 \\
+    Tournament Sample & 3 & 4 \\
+    Open Reproduction Rate & NA & 5 \\
+    Closed Reproduction Rate & NA & 45 \\
+    Max Age & NA & 80 \\
+    Base Approval & NA & 80 \\
+    Goal Approval & NA & 100
     \end{tabular}
@@
 
-    \begin{table}[]
-        \centering        
-        \caption{LifeCycle Algorithm configuration.}\label{tab2}
-        \begin{tabular}{|l|l|}
-        \hline
-        \multicolumn{2}{|l|}{LifeCycle   Algorithm} \\ \hline
-        Population & 60 \\ \hline
-        Max   Generation & 20 \\ \hline
-        Stagnation & Off \\ \hline
-        Chromosome   Length & 20 \\ \hline
-        Target   Fitness & 20 \\ \hline
-        Crossover   Rate & 100 \\ \hline
-        Mutation   Rate & 7 \\ \hline
-        Tourney   Reprod. Rate & 50 \\ \hline
-        Tourney   Sample & 4 \\ \hline
-        Max   Age & 80 \\ \hline
-        Open   Reprod. Rate & 5 \\ \hline
-        Closed   Reprod. Rate & 45 \\ \hline
-        Fertility   Rate & 100 \\ \hline
-        Base   Approval & 80 \\ \hline
-        Goal   Approval & 100 \\ \hline
-        Max   Wait Time & 2 \\ \hline
-        \end{tabular}
-        \end{table}
+\subsection{Experiment Results}
 
-\subsection{Results}
+For each experiment, we ran 60 independent executions per algorithm and
+recorded the following results: Last Generation, Total Evaluations, Time
+(seconds), Evaluations/second.
+
+•	Last Gen.: The generation that found the solution.
+•	Eval.: The total number of evaluations the algorithm executed. 
+•	Time (sec): Total elapsed or wall clock time, in seconds. 
+•	Eval/sec: The calculated rate of evaluations per second.
+
+Experiment 1: The goal of our first OneMax experiment was to make sure our
+Life-Cycle algorithm worked as expected, converging on the solution. For this
+experiment, we intentionally used delays (on the tenth of a second magnitude)
+to follow the Life-Cycle algorithm behavior on the console output. For this
+experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
+processes (on containers) where we show the summarized results in Table 2, and
+Figure 5 shows their Box and Whisker chart.
+
+Experiment 2: The goal of our second experiment was to confirm the Life-Cycle
+algorithm continued working as expected, converging on the solution. For this
+experiment, we reduced the time used on delays (now on the thousands of a
+second magnitude) to follow the Life-Cycle algorithm behavior. For this
+experiment, we only used tournament selection for the reproduction, on the
+first configuration running the Life-Cycle on ten processes, versus the second
+configuration where we reduced the processes to the minimum basic 5. We show
+the summarized results in Table 3, and Figure 6 shows their Box and Whisker
+chart.
+
+Experiment 3: The goal of our third experiment was to follow and study the
+behavior of the Life-Cycle algorithm that continued converging on the solution.
+For this experiment, we remained using minimal delays (thousands of a second
+magnitude). For this experiment, we only used tournament selection for the
+reproduction, on the first configuration running the Life-Cycle on six
+processes, two of whom was the Death stage, versus the second configuration
+where we reduced the processes to the minimum (five) but increasing the (Death)
+goal approval range to 115. We show the summarized results in Table 4, and
+Figure 7 shows their Box and Whisker chart.
+
+Experiment 4: The goal of our fourth and last experiment was to follow and
+study the behavior of the Life-Cycle algorithm that continued converging on the
+solution. For this experiment, we remained using minimal delays (thousands of a
+second magnitude). For this experiment, we compared the OneMax DEAP
+implementation versus the Life-Cycle algorithm, only using tournament selection
+for the reproduction, with the Life-Cycle configuration running on the minimum
+(five) processes but increasing the (Death) goal approval range to 125. We show
+the summarized results in Table 5, and Figure 8 shows their Box and Whisker
+chart.
+
     Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.

### 2021-09-28 paper.tex
Work in progress
Experiment charts upload

@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig5_processes_containers .pdf}
+    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
     \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig5}
@@
 processes (on containers) where we show the summarized results in Table 2, and
-Figure 5 shows their Box and Whisker chart.
+Figure 6 shows their Box and Whisker chart.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}
+    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle (10 processes).} \label{fig6}
+    \end{figure}
 
@@
 configuration where we reduced the processes to the minimum basic 5. We show
-the summarized results in Table 3, and Figure 6 shows their Box and Whisker
+the summarized results in Table 3, and Figure 7 shows their Box and Whisker
 chart.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}
+    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
+    \end{figure}
 
@@
 goal approval range to 115. We show the summarized results in Table 4, and
-Figure 7 shows their Box and Whisker chart.
+Figure 8 shows their Box and Whisker chart.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}
+    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 proc. Death x2, versus 5 proc. w/115 goal).} \label{fig8}
+    \end{figure}
 
@@
 (five) processes but increasing the (Death) goal approval range to 125. We show
-the summarized results in Table 5, and Figure 8 shows their Box and Whisker
+the summarized results in Table 5, and Figure 9 shows their Box and Whisker
 chart.
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}
+    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 proc. w/125 goal).} \label{fig9}
+    \end{figure}
+
+The following tables will be removed from the document.
 

### 2021-09-28 paper.tex
Work in progress
Still working.

@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+\DeclareUnicodeCharacter{2212}{-}
+\DeclareUnicodeCharacter{22C5}{-}
 
@@
     \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab1}
-    \begin{tabular}{lll}
-    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\
-    Population & 60 & 60 \\
-    Max Generation & 20 & 20 \\
-    Stagnation & Off & 10 \\
-    Chromosome Length & 20 & 20 \\
-    Target Fitness & 20 & 20 \\
-    Crossover Rate & 100 & 100 \\
-    Mutation Rate & 7 & 7 \\
-    Tournament Rate & 100 & 50 \\
-    Tournament Sample & 3 & 4 \\
-    Open Reproduction Rate & NA & 5 \\
-    Closed Reproduction Rate & NA & 45 \\
-    Max Age & NA & 80 \\
-    Base Approval & NA & 80 \\
-    Goal Approval & NA & 100
+    \begin{tabular}{|l|l|l|}
+    \hline
+    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
+    Population & 60 & 60 \\ \hline
+    Max Generation & 20 & 20 \\ \hline
+    Stagnation & Off & 10 \\ \hline
+    Chromosome Length & 20 & 20 \\ \hline
+    Target Fitness & 20 & 20 \\ \hline
+    Crossover Rate & 100 & 100 \\ \hline
+    Mutation Rate & 7 & 7 \\ \hline
+    Tournament Rate & 100 & 50 \\ \hline
+    Tournament Sample & 3 & 4 \\ \hline
+    Open Reproduction Rate & NA & 5 \\ \hline
+    Closed Reproduction Rate & NA & 45 \\ \hline
+    Max Age & NA & 80 \\ \hline
+    Base Approval & NA & 80 \\ \hline
+    Goal Approval & NA & 100 \\ \hline
     \end{tabular}

### 2021-09-28 paper.tex
Work in progress
Update

@@
 reproduction). We use many combinations of the containerized processes, up to
-the minimum number required to obtain good results. Figure 4 shows a comparison
+the minimum number required to obtain good results. Figure 5 shows a comparison
 of only two alternatives for the implementation of the algorithm. Our
 experimentation started with a configuration of ten processes and ended in
-five, shown on the left and right sides of figure 4, respectively.
+five, shown on the left and right sides of figure 5, respectively.
 

### 2021-09-28 paper.tex
Work in progress
Experiment tables update

@@
 newborn to an aged adult, where the individual's fitness will impact their
-longevity.
+longevity. The general model concept is shown on the Fig.~\ref{fig2}.
 
@@
 
-The figure 4 describes the general flowchart for the Life-Cycle algorithm.
+The Figure~\ref{fig4} describes the general flowchart for the Life-Cycle algorithm.
 
@@
 reproduction). We use many combinations of the containerized processes, up to
-the minimum number required to obtain good results. Figure 5 shows a comparison
+the minimum number required to obtain good results. Figure~\ref{fig5} shows a comparison
 of only two alternatives for the implementation of the algorithm. Our
 experimentation started with a configuration of ten processes and ended in
-five, shown on the left and right sides of figure 5, respectively.
+five, shown on the left and right sides of Fig.~\ref{fig5}, respectively.
 
@@
 experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
-processes (on containers) where we show the summarized results in Table 2, and
-Figure 6 shows their Box and Whisker chart.
+processes (on containers) where we show the summarized results in Table~\ref{tab2}, and
+Figure~\ref{fig6} shows their Box and Whisker chart.
+
+\begin{table}[]
+    \centering        
+    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab2}
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (10P)} \\ \hline
+    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
+    Avg. & 6.5 & 391 & 0.036 & 10,836 & 9.6 & 578 & 6.830 & 85 \\ \hline
+    \end{tabular}
+    \end{table}
 
@@
 configuration where we reduced the processes to the minimum basic 5. We show
-the summarized results in Table 3, and Figure 7 shows their Box and Whisker
+the summarized results in Table~\ref{tab3}, and Figure~\ref{fig7} shows their Box and Whisker
 chart.
+
+\begin{table}[]
+    \centering        
+    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab3}
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 10P)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P)} \\ \hline
+    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
+    Avg. & 7.2 & 434 & 0.740 & 587 & 8.2 & 495 & 0.826 & 599 \\ \hline
+    \end{tabular}
+    \end{table}
 
@@
 where we reduced the processes to the minimum (five) but increasing the (Death)
-goal approval range to 115. We show the summarized results in Table 4, and
-Figure 8 shows their Box and Whisker chart.
+goal approval range to 115. We show the summarized results in Table~\ref{tab4}, and
+Figure~\ref{fig8} shows their Box and Whisker chart.
+
+\begin{table}[]
+    \centering        
+    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab4}
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 6P, Death x2)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P, 80-115g)} \\ \hline
+    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
+    Avg. & 8.0 & 483 & 0.846 & 571 & 6.4 & 384 & 0.695 & 553 \\ \hline
+    \end{tabular}
+    \end{table}
 
@@
 (five) processes but increasing the (Death) goal approval range to 125. We show
-the summarized results in Table 5, and Figure 9 shows their Box and Whisker
+the summarized results in Table~\ref{tab5}, and Figure~\ref{fig9} shows their Box and Whisker
 chart.
+
+\begin{table}[]
+    \centering        
+    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab5}
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (Tourn. 5P, 80-125g)} \\ \hline
+    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
+    Avg. & 6.5 & 391 & 0.036 & 10,836 & 6.3 & 377 & 0.678 & 556 \\ \hline
+    \end{tabular}
+    \end{table}
 
@@
         \centering        
-        \caption{OneMax DEAP experiment results.}\label{tab3}        
+        \caption{OneMax DEAP experiment results.}\label{tab6}        
         \begin{tabular}{|l|l|l|l|l|}
@@
         \centering        
-        \caption{LifeCycle Algorithm experiment results.}\label{tab4}
+        \caption{LifeCycle Algorithm experiment results.}\label{tab7}
         \begin{tabular}{|l|l|l|l|l|}

### 2021-09-28 paper.tex
Work in progress
General tables and images upgrade.

@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig1_background.pdf}
+    \centering
+    \includegraphics[width=80mm]{img/fig1_background.pdf}
     \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig2_proposal.pdf}
+    \centering
+    \includegraphics[width=70mm]{img/fig2_proposal.pdf}
     \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig2}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig3_newtonslaw.pdf}
+    \centering
+    \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
     \caption{Newton's Law of Universal Gravitation.} \label{fig3}
@@
 Where:
-•	F is the gravitational force acting between two objects
-•	m1 and m2 are the masses of the objects
-•	r is the distance between the centers of their masses
-•	G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2
+\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
+    \item[$\bullet$ F] is the gravitational force acting between two objects
+    \item[$\bullet$ m1 and m2] are the masses of the objects
+    \item[$\bullet$ r]	is the distance between the centers of their masses
+    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2
+\end{description}
 
@@
 recorded the following results: Last Generation, Total Evaluations, Time
-(seconds), Evaluations/second.
+(seconds), Evaluations/second. The labels used on the table header are the
+following:
 
-•	Last Gen.: The generation that found the solution.
-•	Eval.: The total number of evaluations the algorithm executed. 
-•	Time (sec): Total elapsed or wall clock time, in seconds. 
-•	Eval/sec: The calculated rate of evaluations per second.
+\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
+    \item[$\bullet$ Last Gen.:] The generation that found the solution.
+    \item[$\bullet$ Eval.:] The total number of evaluations the algorithm executed. 
+    \item[$\bullet$ Time (sec):] Total elapsed or wall clock time, in seconds. 
+    \item[$\bullet$ Eval/sec:] The calculated rate of evaluations per second.
+\end{description}
 
@@
 
-The following tables will be removed from the document.
-
-    Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.
-
-    \begin{table}[]
-        \centering        
-        \caption{OneMax DEAP experiment results.}\label{tab6}        
-        \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \multicolumn{5}{|c|}{\textbf{OneMax DEAP}} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
-        1 & 6 & 20 & 360 & 0.016 \\ \hline
-        2 & 5 & 20 & 300 & 0.032 \\ \hline
-        3 & 7 & 20 & 420 & 0.061 \\ \hline
-        4 & 9 & 20 & 540 & 0.081 \\ \hline
-        5 & 8 & 20 & 480 & 0.080 \\ \hline
-        6 & 6 & 20 & 360 & 0.062 \\ \hline
-        7 & 7 & 20 & 420 & 0.062 \\ \hline
-        8 & 6 & 20 & 360 & 0.016 \\ \hline
-        9 & 8 & 20 & 480 & 0.058 \\ \hline
-        10 & 6 & 20 & 360 & 0.050 \\ \hline
-        11 & 7 & 20 & 420 & 0.073 \\ \hline
-        12 & 8 & 20 & 480 & 0.076 \\ \hline
-        13 & 8 & 20 & 480 & 0.065 \\ \hline
-        14 & 6 & 20 & 360 & 0.060 \\ \hline
-        15 & 6 & 20 & 360 & 0.045 \\ \hline
-        16 & 6 & 20 & 360 & 0.059 \\ \hline
-        17 & 6 & 20 & 360 & 0.061 \\ \hline
-        18 & 6 & 20 & 360 & 0.058 \\ \hline
-        19 & 5 & 20 & 300 & 0.060 \\ \hline
-        20 & 7 & 20 & 420 & 0.067 \\ \hline
-        21 & 7 & 20 & 420 & 0.060 \\ \hline
-        22 & 7 & 20 & 420 & 0.085 \\ \hline
-        23 & 7 & 20 & 420 & 0.071 \\ \hline
-        24 & 4 & 20 & 300 & 0.049 \\ \hline
-        25 & 6 & 20 & 360 & 0.050 \\ \hline
-        26 & 9 & 20 & 540 & 0.081 \\ \hline
-        27 & 6 & 20 & 420 & 0.074 \\ \hline
-        28 & 6 & 20 & 360 & 0.064 \\ \hline
-        29 & 6 & 20 & 360 & 0.065 \\ \hline
-        30 & 4 & 20 & 240 & 0.016 \\ \hline
-        Avg. & 6.5 & 20 & 394 & 0.059 \\ \hline
-        \end{tabular}
-        \end{table}
-
-    \begin{table}[]
-        \centering        
-        \caption{LifeCycle Algorithm experiment results.}\label{tab7}
-        \begin{tabular}{|l|l|l|l|l|}
-        \hline
-        \multicolumn{5}{|c|}{\textbf{LifeCycle Algorithm}} \\ \hline
-        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
-        1 & 8 & 20 & 486 & 6.65 \\ \hline
-        2 & 6 & 20 & 381 & 5.20 \\ \hline
-        3 & 6 & 20 & 369 & 5.69 \\ \hline
-        4 & 7 & 20 & 434 & 6.37 \\ \hline
-        5 & 12 & 20 & 731 & 8.20 \\ \hline
-        6 & 5 & 20 & 306 & 4.55 \\ \hline
-        7 & 13 & 20 & 764 & 8.34 \\ \hline
-        8 & 4 & 20 & 233 & 4.09 \\ \hline
-        9 & 12 & 20 & 692 & 7.27 \\ \hline
-        10 & 6 & 20 & 338 & 4.76 \\ \hline
-        11 & 9 & 20 & 559 & 7.78 \\ \hline
-        12 & 12 & 20 & 730 & 8.35 \\ \hline
-        13 & 4 & 20 & 219 & 3.43 \\ \hline
-        14 & 8 & 20 & 462 & 5.28 \\ \hline
-        15 & 4 & 20 & 217 & 3.37 \\ \hline
-        16 & 4 & 20 & 234 & 4.54 \\ \hline
-        17 & 4 & 20 & 256 & 4.35 \\ \hline
-        18 & 12 & 20 & 714 & 8.14 \\ \hline
-        19 & 12 & 20 & 694 & 7.88 \\ \hline
-        20 & 15 & 20 & 892 & 9.74 \\ \hline
-        21 & 11 & 20 & 633 & 7.98 \\ \hline
-        22 & 3 & 20 & 169 & 4.02 \\ \hline
-        23 & 10 & 20 & 611 & 6.89 \\ \hline
-        24 & 10 & 20 & 629 & 7.32 \\ \hline
-        25 & 7 & 20 & 416 & 6.22 \\ \hline
-        26 & 7 & 20 & 446 & 5.55 \\ \hline
-        27 & 6 & 20 & 379 & 5.95 \\ \hline
-        28 & 8 & 20 & 466 & 6.98 \\ \hline
-        29 & 3 & 20 & 197 & 3.36 \\ \hline
-        30 & 6 & 20 & 381 & 6.16 \\ \hline
-        Avg. & 7.8 & 20 & 468 & 6.15 \\ \hline
-        \end{tabular}
-        \end{table}
+% Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.
 

### 2021-09-28 paper.tex
Work in progress
New Experiments Chart border

@@
 \begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
-    \item[$\bullet$ F] is the gravitational force acting between two objects
-    \item[$\bullet$ m1 and m2] are the masses of the objects
-    \item[$\bullet$ r]	is the distance between the centers of their masses
-    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2
+    \item[$\bullet$ F] is the gravitational force acting between two objects.
+    \item[$\bullet$ m1 and m2] are the masses of the objects.
+    \item[$\bullet$ r]	is the distance between the centers of their masses.
+    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
 \end{description}
@@
 recorded the following results: Last Generation, Total Evaluations, Time
-(seconds), Evaluations/second. The labels used on the table header are the
-following:
+(seconds), Evaluations/second. The labels used on the header of the results of
+our summarized experiments tables are the following:
 
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}
+    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
     \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle (10 processes).} \label{fig6}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}
+    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
     \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}
+    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
     \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 proc. Death x2, versus 5 proc. w/115 goal).} \label{fig8}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}
+    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
     \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 proc. w/125 goal).} \label{fig9}

### 2021-09-28 paper.tex
Work in progress
Experiment labels improvement.

@@
     \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle (10 processes).} \label{fig6}
+    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig6}
     \end{figure}
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 proc. Death x2, versus 5 proc. w/115 goal).} \label{fig8}
+    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig8}
     \end{figure}
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 proc. w/125 goal).} \label{fig9}
+    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig9}
     \end{figure}

### 2021-09-29 paper.tex
Work in progress
Sorted bib file

@@
 process, which is flexible to work in parallel with multiple couple selection
-methods, for example, tournament selection, random selection (closed
-reproduction), and couple match by creating a new mating individual (open
-reproduction). We use many combinations of the containerized processes, up to
-the minimum number required to obtain good results. Figure~\ref{fig5} shows a comparison
-of only two alternatives for the implementation of the algorithm. Our
-experimentation started with a configuration of ten processes and ended in
-five, shown on the left and right sides of Fig.~\ref{fig5}, respectively.
+methods, for example, tournament selection, random selection (Closed
+Reproduction process), and couple match by creating a new mating individual
+(Open Reproduction process). We use many combinations of the containerized
+processes, up to the minimum number required to obtain good results.
+Figure~\ref{fig5} shows a comparison of only two alternatives for the
+implementation of the algorithm. Our experimentation started with a
+configuration of ten processes and ended in five, shown on the left and right
+sides of Fig.~\ref{fig5}, respectively.
 
@@
 recorded the following results: Last Generation, Total Evaluations, Time
-(seconds), Evaluations/second. The labels used on the header of the results of
-our summarized experiments tables are the following:
+(seconds), Evaluations/second. The labels used on the results of our summarized
+experiments tables are the following:
 

### 2021-09-29 paper.tex
Work in progress
Minor text improvement.

@@
 reproduction, on the first configuration running the Life-Cycle on six
-processes, two of whom was the Death stage, versus the second configuration
+processes, two of whom was the Death process, versus the second configuration
 where we reduced the processes to the minimum (five) but increasing the (Death)
-goal approval range to 115. We show the summarized results in Table~\ref{tab4}, and
-Figure~\ref{fig8} shows their Box and Whisker chart.
+goal approval range to 115. We show the summarized results in Table~\ref{tab4},
+and Figure~\ref{fig8} shows their Box and Whisker chart.
 

### 2021-09-29 paper.tex
Work in progress
Discussion improvement

@@
 
-In our experiments, we found that for simple problems, the cost of
-communication between containers will increase the total time of execution,
-however, we believe that the opposite must also be true: for complex problems,
-distributing the work on multiple resources must reduce time, making the
-communication cost negligible.
+We must acknowledge the performance time of the DEAP library is highly
+efficient and short, due in part because the processing work execution is on a
+single processor with multiple cores, where the communication time is nearly
+non-existent. In contrast, our algorithm implementation requires a minimum of
+five containers and a message queue server. Even though the container work has
+proven to be very effective and efficient [X], we must consider some time was
+added to our experiments by the minimal delays (in the thousands of a second
+magnitude) we used to keep the process execution relatively random, to mimic
+how the life-cycle stages work in nature. As future work, we could test the
+Life-Cycle algorithm behavior by eliminating all remaining delays.
+
+In our experiments, we found that when solving simple problems, the cost of
+communication between containers can become a factor to increase the total
+performance time, even though, we believe that the opposite must also be true.
+When solving complex problems, distributing the work on multiple resources
+should reduce throughput time, making the communication cost negligible.
 

### 2021-09-29 paper.tex
Work in progress
Minor improvement

@@
 
-In this experiment, we needed to match or balance the experimentation
+In our four experiments, we needed to match or balance the experimentation
 parameters according to the specifications of the algorithm used by the DEAP

### 2021-09-29 paper.tex
Work in progress
Proposal improvement

@@
 \section{Proposal}
+
+Our main inspiration for this algorithm was born from the study and observation
+of nature, where many successful (AI) algorithms have previously found their
+inspiration. Our focus was not on a single animal species but all of them,
+using general abstraction to identify what those species have in common. In our
+analysis, we consider a broad animal spectrum, from bacteria to humans and
+lions, finding our inspiration on the biological Life Cycle of the animal
+species.
 

### 2021-09-29 paper.tex
Work in progress
Proposal improvement

@@
 Our main inspiration for this algorithm was born from the study and observation
-of nature, where many successful (AI) algorithms have previously found their
-inspiration. Our focus was not on a single animal species but all of them,
-using general abstraction to identify what those species have in common. In our
-analysis, we consider a broad animal spectrum, from bacteria to humans and
-lions, finding our inspiration on the biological Life Cycle of the animal
+of nature, where many successful optimization algorithms have previously found
+their inspiration. Our focus was not on a single animal species but all of
+them, using general abstraction to identify what those species have in common.
+In our analysis, we consider a broad animal spectrum, from bacteria to humans
+and lions, finding our inspiration on the biological Life Cycle of the animal
 species.

### 2021-09-29 paper.tex
Work in progress
References upgrade

@@
 Our algorithm works on a constantly evolving population, experiencing the
-stages that all living beings undergo: being born, growing up, reproducing, and
+stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and
 dying, where each of these stages will be processes (of our algorithm) that
@@
 In this paper, we present an algorithm inspired by the biological Life-Cycle of
-animal species, which consists of several stages: birth, growth, reproduction,
+animal species, which consists of several stages \cite{read1968system}: birth, growth, reproduction,
 and death. As in nature, we intend to execute all these stages in parallel and
@@
 solving the OneMax problem to compare it with a traditional GA algorithm using
-the DEAP (Distributed Evolutionary Algorithms in Python) library. The OneMax
-problem uses a genetic algorithm to evolve a population of randomly generated
+the DEAP (Distributed Evolutionary Algorithms in Python) library
+\cite{fortin2012deap}. The OneMax problem \cite{krejca2020lower,witt2019upper}
+uses a genetic algorithm to evolve a population of randomly generated
 individuals with zeros and ones, and it stops until a solution of only ones is
@@
 
-We must acknowledge the performance time of the DEAP library is highly
-efficient and short, due in part because the processing work execution is on a
-single processor with multiple cores, where the communication time is nearly
-non-existent. In contrast, our algorithm implementation requires a minimum of
-five containers and a message queue server. Even though the container work has
-proven to be very effective and efficient [X], we must consider some time was
-added to our experiments by the minimal delays (in the thousands of a second
-magnitude) we used to keep the process execution relatively random, to mimic
-how the life-cycle stages work in nature. As future work, we could test the
-Life-Cycle algorithm behavior by eliminating all remaining delays.
+We must acknowledge the performance time of the DEAP library
+\cite{fortin2012deap} is highly efficient and short, due in part because the
+processing work execution is on a single processor with multiple cores, where
+the communication time is nearly non-existent. In contrast, our algorithm
+implementation requires a minimum of five containers and a message queue
+server. Even though the container work has proven to be very effective and
+efficient [X], we must consider some time was added to our experiments by the
+minimal delays (in the thousands of a second magnitude) we used to keep the
+process execution relatively random, to mimic how the life-cycle stages work in
+nature \cite{read1968system}. As future work, we could test the Life-Cycle
+algorithm behavior by eliminating all remaining delays.
 
@@
 use control or some more complex and demanding problem that requires computing
-real numbers.
+real numbers \cite{stanley2002evolving,miikkulainen2019evolving}.
 

### 2021-09-29 paper.tex
Work in progress
Proposal upgrade

@@
 them, using general abstraction to identify what those species have in common.
+
 In our analysis, we consider a broad animal spectrum, from bacteria to humans
 and lions, finding our inspiration on the biological Life Cycle of the animal
-species.
-
-In this paper, we present an algorithm inspired by the biological Life-Cycle of
-animal species, which consists of several stages \cite{read1968system}: birth, growth, reproduction,
-and death. As in nature, we intend to execute all these stages in parallel and
-asynchronously on a population that evolves constantly.
+species, which consists of several stages \cite{read1968system}: birth, growth,
+reproduction, and death. As in nature, we intend to execute all these stages in
+parallel and asynchronously on a population that evolves constantly. The
+combination of those processes is what we call evolution.
 

### 2021-09-29 paper.tex
Work in progress
Proposal upgrade

@@
 of nature, where many successful optimization algorithms have previously found
-their inspiration. Our focus was not on a single animal species but all of
-them, using general abstraction to identify what those species have in common.
+their own. Our focus was not on a single animal species but all of them, using
+general abstraction to identify what those species have in common.
 
@@
 
-From the ground up, we designed the algorithm as a cloud-native solution using
-the cloud available resources to divide the processing workload, among several
-computers or running the algorithm as a cloud service. The algorithm works
-concurrently and asynchronously on a constantly evolving population, using
-different computers (or containers) independently, theoretically eliminating
-waiting times between processes.
+One of the main challenges when designing the algorithm was how to capture the
+essence of life by reflecting a population evolution?. In our minds, it was
+clear this task requires a combination of simultaneous working forces that
+influences the population improvement over time. Our strategy was simple:
+divide and conquer, looking into the clouds. Enter cloud-computing: previous
+cloud-computing algorithms have proven successful results working in
+optimization problems \cite{garcia2021event}.
+
+We turned back to our genetic algorithms knowledge, mixed with our inspiration
+and cloud computing, and designed the algorithm with the quest to divide the
+processing workload among multiple computers. This strategy would also make it
+possible to run our algorithm as a cloud service. Theoretically, one
+consequence of the workload distribution is to obtain lower execution times.
 

### 2021-09-29 paper.tex
Work in progress
Figure legend update
Work in progress
Figure legend upgrade
Work in progress
Proposal and discussion improvement.

@@
 their own. Our focus was not on a single animal species but all of them, using
-general abstraction to identify what those species have in common.
+general abstraction to identify what those species have in common. Some
+questions in our train of thought were:
+
+\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
+    \item[$\cdot$] How does nature work?
+    \item[$\cdot$] Is evolution real?
+    \item[$\cdot$] How do we enforce natural selection in evolution?
+    \item[$\cdot$] What is the role of the attraction between couples on reproduction?
+    \item[$\cdot$] How much of a factor is the attraction's role in the evolution of the species?
+    \item[$\cdot$] What is the role of death in all of this?
+    \item[$\cdot$] How much of an impact does death have on the evolution of a species?
+    \item[$\cdot$] How do we include those ideas into our algorithm?
+\end{description}
 
@@
 newborn to an aged adult, where the individual's fitness will impact their
-longevity. The general model concept is shown on the Fig.~\ref{fig2}.
+longevity. The general model concept is shown in Figure~\ref{fig2}.
 
@@
 
+At some crucial moments during our research, we got the feeling we were doing
+nature reverse engineering. One strategy was to let our imagination run wild
+and go for the simple solution. One of our earlier experiment's findings was to
+find balance, like the yin and yang, between death and reproduction.
+
+In our experiments, we found that when solving simple problems, the cost of
+communication between containers can become a factor to increase the total
+performance time, even though, we believe that the opposite must also be true.
+When solving complex problems, distributing the work on multiple resources
+should reduce throughput time, making the communication cost negligible.
+
 We must acknowledge the performance time of the DEAP library
@@
 algorithm behavior by eliminating all remaining delays.
-
-In our experiments, we found that when solving simple problems, the cost of
-communication between containers can become a factor to increase the total
-performance time, even though, we believe that the opposite must also be true.
-When solving complex problems, distributing the work on multiple resources
-should reduce throughput time, making the communication cost negligible.
 

### 2021-09-29 paper.tex
Work in progress
Background check
Work in progress
Description and Background update

@@
 
-\section{Description of the sections of the Paper}
+\section{Description} 
+% Description of the sections of the Paper
+% We structure this research paper as follows
 
-\section{State of the art}
+We present the description of the following sections in our research paper.
 
-Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.
+\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
+    \item[$\cdot Background$] We do a brief explanation of our motivation for this research.
+    \item[$\cdot Proposal$] We present an algorithm inspired by the Life-Cycle of animal species.
+    \item[$\cdot Experiments$] We specify our experimental setup, configuration, and results.
+    \item[$\cdot Discussion$] We analyze and describe some of our research findings.
+    \item[$\cdot Conclusions$] We present some inferences based on our experiments' results.
+    \item[$\cdot References$] We enumerate the references for our research paper.
+\end{description}
+
+\section{Background}
 
@@
 % \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-
-\subsection{Background}
+% Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.
 
@@
 cloud-native optimization framework, that can include multiple
-(population-based) algorithms~\cite{valdez2021container}. In their research, they work with ideas such
-as those mentioned in Fig.~\ref{fig1}.
+(population-based) algorithms~\cite{valdez2021container}. In their research,
+they work with ideas such as those mentioned in Figure~\ref{fig1}.
 

### 2021-09-29 paper.tex
Work in progress
Proposal improvement.

@@
 their own. Our focus was not on a single animal species but all of them, using
-general abstraction to identify what those species have in common. Some
-questions in our train of thought were:
+general abstraction to identify what those species have in common.
 
-\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
-    \item[$\cdot$] How does nature work?
-    \item[$\cdot$] Is evolution real?
-    \item[$\cdot$] How do we enforce natural selection in evolution?
-    \item[$\cdot$] What is the role of the attraction between couples on reproduction?
-    \item[$\cdot$] How much of a factor is the attraction's role in the evolution of the species?
-    \item[$\cdot$] What is the role of death in all of this?
-    \item[$\cdot$] How much of an impact does death have on the evolution of a species?
-    \item[$\cdot$] How do we include those ideas into our algorithm?
-\end{description}
+Some questions in our train of thought were: How does nature work? Is evolution
+real? How do we enforce natural selection in evolution? What is the role of the
+attraction between couples on reproduction? How much of a factor is the
+attraction's role in the evolution of the species? What is the role of death in
+all of this? How much of an impact does death have on the evolution of a
+species? How do we include those ideas into our algorithm?
 

### 2021-09-30 paper.tex
Work in progress
Introduction update

@@
 bio-inspired algorithms are designed with a traditionally sequential
-perspective, where each process must wait for the previous task to finish
+perspective [X-Z], where each process must wait for the previous task to finish
 before continuing. Some architectures address this issue, what distinguishes
@@
 Our algorithm works on a constantly evolving population, experiencing the
-stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and
-dying, where each of these stages will be processes (of our algorithm) that
-randomly affect the population individuals, emulating the organic way.
+stages that all living beings undergo \cite{read1968system}: being born,
+growing up, reproducing, and dying, where each of these stages will be
+processes (of our algorithm) that randomly affect the population individuals,
+emulating the organic way.
 
-In this research, we seek to demonstrate that it is possible to evolve a
-population of individuals, similar to a Genetic Algorithm (GA), using a
-distributed, parallel, and asynchronous methodology.
+The main contribution of the paper is to design and create a new algorithm with
+the purpose to demonstrate that it is possible to evolve a population of
+individuals, similar to a Genetic Algorithm (GA), using a distributed,
+parallel, and asynchronous methodology by implementation and testing of the
+algorithm.
 
-\section{Description} 
-% Description of the sections of the Paper
-% We structure this research paper as follows
-
-We present the description of the following sections in our research paper.
-
-\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
-    \item[$\cdot Background$] We do a brief explanation of our motivation for this research.
-    \item[$\cdot Proposal$] We present an algorithm inspired by the Life-Cycle of animal species.
-    \item[$\cdot Experiments$] We specify our experimental setup, configuration, and results.
-    \item[$\cdot Discussion$] We analyze and describe some of our research findings.
-    \item[$\cdot Conclusions$] We present some inferences based on our experiments' results.
-    \item[$\cdot References$] We enumerate the references for our research paper.
-\end{description}
+We present the description of the following sections in our paper. First, we do
+a brief explanation of our motivation for this research in section 2, next, we
+present our algorithm inspired by the Life-Cycle of animal species in section
+3, followed by our experimental configuration and results in section 4, then we
+analyze and describe some of our research findings in section 5, and we
+finalize by presenting some inferences based on our experiments' results in
+section 6.
 

### 2021-09-30 paper.tex
Work in progress
Abstract double check: removed dash added from a (PDF document) copy paste.

@@
 Several bio-inspired algorithms use population evolution as analogies of
-na-ture. In this paper, we present an algorithm inspired by the biological
+nature. In this paper, we present an algorithm inspired by the biological
 Life-Cycle of animal species, which consists of several stages: birth, growth,
-re-production, and death. As in nature, we intend to execute all these stages
-in parallel and asynchronously on a population that evolves constantly. From
-the ground up, we designed the algorithm as a cloud-native solution using the
-cloud available resources to divide the processing workload, among several
-computers or running the algorithm as a cloud service. The algorithm works
-concurrently and asynchronously on a constantly evolving population, using
-different computers (or containers) independently, eliminating waiting times
-between processes. This algorithm seeks to imitate the natural life cycle,
-where new individuals are born at any moment and mature over time, where they
-age and suffer mutations throughout their lives. In reproduction, couples match
-by mutual attraction, where they may have offspring. Death can happen to
-everyone: from a newborn to an aged adult, where the individual's fitness will
-impact their longevity. As a proof-of-concept, we implemented the algo-rithm
-with Docker containers by solving the OneMax problem comparing it with a basic
-(sequential) GA algorithm, where it showed favorable and prom-ising results.
+reproduction, and death. As in nature, we intend to execute all these stages in
+parallel and asynchronously on a population that evolves constantly. From the
+ground up, we designed the algorithm as a cloud-native solution using the cloud
+available resources to divide the processing workload among several computers
+or running the algorithm as a cloud service. The algorithm works concurrently
+and asynchronously on a constantly evolving population, using different
+computers (or containers) independently, eliminating waiting times between
+processes. This algorithm seeks to imitate the natural life cycle, where new
+individuals are born at any moment and mature over time, where they age and
+suffer mutations throughout their lives. In reproduction, couples match by
+mutual attraction, where they may have offspring. Death can happen to everyone:
+from a newborn to an aged adult, where the individual's fitness will impact
+their longevity. As a proof-of-concept, we implemented the algorithm with
+Docker containers by solving the OneMax problem comparing it with a basic
+(sequential) GA algorithm, where it showed favorable and promising results.
 

### 2021-09-30 paper.tex
Work in progress
Minor stetic updates

@@
 \begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
-    \item[$\bullet$ Last Gen.:] The generation that found the solution.
-    \item[$\bullet$ Eval.:] The total number of evaluations the algorithm executed. 
-    \item[$\bullet$ Time (sec):] Total elapsed or wall clock time, in seconds. 
-    \item[$\bullet$ Eval/sec:] The calculated rate of evaluations per second.
+    \item[$\bullet $Last Gen.] is the generation that found the solution.
+    \item[$\bullet $Eval.] is the total number of evaluations the algorithm executed. 
+    \item[$\bullet $Time (sec)] is the total elapsed or wall clock time, in seconds. 
+    \item[$\bullet $Eval/sec] is the calculated rate of evaluations per second.
 \end{description}

### 2021-09-30 paper.tex
Work in progress
Reference update.

@@
 Bio-inspired algorithms have been very successful when used to solve complex
-optimization problems, but as their complexity increases so does the computing
-power required. One strategy to address this processing need is to use
-distributed computing, or the resources available in the cloud to help find the
-solution. This strategy gives us elasticity to adjust (increase or reduce) the
-computing power to achieve a balance according to the nature of the problem.
+optimization problems
+\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
+their complexity increases so does the computing power required
+\cite{ontiveros2018high}. One strategy to address this processing need is to
+use distributed computing \cite{thain2005distributed}, or the resources
+available in the cloud \cite{garcia2013there,eshratifar2019bottlenet} to help
+find the solution. This strategy gives us elasticity to adjust (increase or
+reduce) the computing power to achieve a balance according to the nature of the
+problem \cite{armbrust2010view}.
 
@@
 bio-inspired algorithms are designed with a traditionally sequential
-perspective [X-Z], where each process must wait for the previous task to finish
-before continuing. Some architectures address this issue, what distinguishes
-us, is that our proposal presents an algorithm designed in its entirety as a
-native solution in the cloud, fully distributed, where its processes are
-executed in parallel and asynchronously. This technique makes it easy to scale
-the computing power according to the complexity required by the problem.
+perspective \cite{back1996evolutionary} [X-Z], where each process must wait for
+the previous task to finish before continuing. Some architectures address this
+issue, what distinguishes us, is that our proposal presents an algorithm
+designed in its entirety as a native solution in the cloud, fully distributed,
+where its processes are executed in parallel and asynchronously. This technique
+makes it easy to scale the computing power according to the complexity required
+by the problem.
 
@@
 cloud-computing algorithms have proven successful results working in
-optimization problems \cite{garcia2021event}.
+optimization problems \cite{valdez2021container,garcia2021event}.
 
@@
 server. Even though the container work has proven to be very effective and
-efficient [X], we must consider some time was added to our experiments by the
-minimal delays (in the thousands of a second magnitude) we used to keep the
-process execution relatively random, to mimic how the life-cycle stages work in
-nature \cite{read1968system}. As future work, we could test the Life-Cycle
-algorithm behavior by eliminating all remaining delays.
+efficient \cite{merelo2016performance,valdez2021container}, we must consider
+some time was added to our experiments by the minimal delays (in the thousands
+of a second magnitude) we used to keep the process execution relatively random,
+to mimic how the life-cycle stages work in nature \cite{read1968system}. As
+future work, we could test the Life-Cycle algorithm behavior by eliminating all
+remaining delays.
 

### 2021-09-30 paper.tex
Work in progress
References update

@@
 reduce) the computing power to achieve a balance according to the nature of the
-problem \cite{armbrust2010view}.
+problem.
 
@@
 the previous task to finish before continuing. Some architectures address this
-issue, what distinguishes us, is that our proposal presents an algorithm
-designed in its entirety as a native solution in the cloud, fully distributed,
-where its processes are executed in parallel and asynchronously. This technique
-makes it easy to scale the computing power according to the complexity required
-by the problem.
+issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
+distinguishes us, is that our proposal presents an algorithm designed in its
+entirety as a native solution in the cloud, fully distributed, where its
+processes are executed in parallel and asynchronously. This technique makes it
+easy to scale the computing power according to the complexity required by the
+problem \cite{armbrust2010view}.
 

### 2021-09-30 paper.tex
Work in progress
References improvement

@@
 bio-inspired algorithms are designed with a traditionally sequential
-perspective \cite{back1996evolutionary} [X-Z], where each process must wait for
-the previous task to finish before continuing. Some architectures address this
-issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
+perspective \cite{porto2018evolutionary,back1996evolutionary}, where each
+process must wait for the previous task to finish before continuing. Some
+architectures address this issue
+\cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
 distinguishes us, is that our proposal presents an algorithm designed in its
@@
 
-One of the publications with the most influence on our research proposes a
-cloud-native optimization framework, that can include multiple
-(population-based) algorithms~\cite{valdez2021container}. In their research,
-they work with ideas such as those mentioned in Figure~\ref{fig1}.
+Many of the publications with the most influence on our research
+~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
+propose a cloud-native optimization architecture that features population-based
+algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
+which planted the seed of thought in our current paper.
 
@@
     \includegraphics[width=80mm]{img/fig1_background.pdf}
-    \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
+    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig1}
     \end{figure}

### 2021-09-30 paper.tex
Work in progress
Never ending update
Work in progress
Gravitational references update.

@@
 algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
-which planted the seed of thought in our current paper.
+which planted the seed of thought of our current paper.
 
@@
 Newton's Law of Universal Gravitation has shown success in helping to solve
-optimization problems.
+optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
 

### 2021-09-30 paper.tex
Final Revisions
Document improvements
Final Updates
Improvements

@@
 %
-\title{A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}}
+\title{A novel distributed nature-inspired algorithm for solving optimization problems}
 % (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
@@
 %
-\authorrunning{F. Author et al.}
+\authorrunning{Felix-Saul et al.}
 % First names are abbreviated in the running head.
@@
 newborn to an aged adult, where the individual's fitness will impact their
-longevity. The general model concept is shown in Figure~\ref{fig2}.
+longevity. The general model concept is shown in Figure~\ref{fig2}. The general
+flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig4}.
 
@@
 for only the best individuals to survive.
-
-\subsection{Life-Cycle algorithm flowchart}
-
-The Figure~\ref{fig4} describes the general flowchart for the Life-Cycle algorithm.
 

### 2021-09-30 paper.tex
ackonledgements section added
Final Updates
Improvements

@@
 Where:
-\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
-    \item[$\bullet$ F] is the gravitational force acting between two objects.
-    \item[$\bullet$ m1 and m2] are the masses of the objects.
-    \item[$\bullet$ r]	is the distance between the centers of their masses.
-    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
-\end{description}
+\begin{itemize}
+    \item[]	    F is the gravitational force acting between two objects.
+    \item[]	    m1 and m2 are the masses of the objects.
+    \item[]	    r is the distance between the centers of their masses.
+    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
+\end{itemize}
 
@@
 
-\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
-    \item[$\bullet $Last Gen.] is the generation that found the solution.
-    \item[$\bullet $Eval.] is the total number of evaluations the algorithm executed. 
-    \item[$\bullet $Time (sec)] is the total elapsed or wall clock time, in seconds. 
-    \item[$\bullet $Eval/sec] is the calculated rate of evaluations per second.
-\end{description}
+\begin{itemize}
+    \item   Last Gen.   is the generation that found the solution.
+    \item   Eval.       is the total number of evaluations the algorithm executed. 
+    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
+    \item   Eval/sec    is the calculated rate of evaluations per second.
+\end{itemize}
 

### 2021-09-30 paper.tex
Final Updates
Background relocation
Final Updates
Introduction improvement

@@
 
-We present the description of the following sections in our paper. First, we do
-a brief explanation of our motivation for this research in section 2, next, we
-present our algorithm inspired by the Life-Cycle of animal species in section
-3, followed by our experimental configuration and results in section 4, then we
-analyze and describe some of our research findings in section 5, and we
+We present the description of the following sections in our paper. First, we
+introduce our algorithm inspired by the Life-Cycle of animal species in section
+2, followed by our experimental configuration and results in section 3, we
+analyze and describe some of our research findings in section 4, and we
 finalize by presenting some inferences based on our experiments' results in
-section 6.
+section 5.
 
-\section{Background}
-
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-% Multiple citations are grouped \cite{valdez2021container,krejca2020lower,witt2019upper,merelo2016nodio,merelo2016performance,fortin2012deap,stanley2002evolving}.
+\section{Proposal}
 
@@
     \end{figure}
-
-\section{Proposal}
 
@@
 
+\section*{Acknowledgments}
+
+This paper has been supported in part by projects DeepBio
+(TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
 %

### 2021-09-30 paper.tex
Final Updates
Section labels and references improvements

@@
 We present the description of the following sections in our paper. First, we
-introduce our algorithm inspired by the Life-Cycle of animal species in section
-2, followed by our experimental configuration and results in section 3, we
-analyze and describe some of our research findings in section 4, and we
-finalize by presenting some inferences based on our experiments' results in
-section 5.
+introduce our algorithm inspired by the Life-Cycle of animal species in
+section~\ref{proposal_section}, followed by our experimental configuration and
+results in section~\ref{experiments_section}, we analyze and describe some of
+our research findings in section~\ref{discussion_section}, and we finalize by
+presenting some inferences based on our experiments' results in
+section~\ref{conclusions_section}.
 
 \section{Proposal}
+\label{proposal_section}
 
@@
 \section{Experiments} 
+\label{experiments_section}
 
@@
 \section{Discussion}
+\label{discussion_section}
 
@@
 \section{Conclusions}
+\label{conclusions_section}
 

### 2021-09-30 paper.tex
Final Update
Minor stetic update

@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
+%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-\documentclass[runningheads]{llncs}
+% sample root file for your "contribution" to a contributed volume
 %
+% Use this file as a template for your own input.
 %
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
+%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[graybox]{svmult}
+
+% choose options for [] as required from the list
+% in the Reference Guide
+
+\usepackage{type1cm}        % activate if the above 3 fonts are
+                            % not available on your system
 %
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{makeidx}         % allows index generation
+\usepackage{graphicx}        % standard LaTeX graphics tool
+                             % when including figure files
+\usepackage{multicol}        % used for the two-column index
+\usepackage[bottom]{footmisc}% places footnotes at page bottom
+
+\usepackage{newtxtext}       % 
+\usepackage{newtxmath}       % selects Times Roman as basic font
+
+% see the list of further useful packages
+% in the Reference Guide
+
+\makeindex             % used for the subject index
+                       % please use the style svind.ist with
+                       % your makeindex program
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{document}
+
+\title*{A novel distributed nature-inspired algorithm for solving optimization problems} 
+\titlerunning{(Biological) Life-Cycle Algorithm}
+% Use \titlerunning{Short Title} for an abbreviated version of
+% your contribution title if the original one is too long
+\author{J. C. Felix-Saul, Mario García Valdez, and Juan J. Merelo Guervós}
+% Use \authorrunning{Short Title} for an abbreviated version of
+% your contribution title if the original one is too long
+\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
+\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
+\and Juan J. Merelo Guervós \at Universidad de Granada, Granada, Spain \email{name@email.address}}
 %
-\title{A novel distributed nature-inspired algorithm for solving optimization problems}
-% (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
+% Use the package "url.sty" to avoid
+% problems with special characters
+% used in your e-mail or web address
 %
-\titlerunning{Life-Cycle Algorithm}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{J. C. Felix-Saul \inst{1} \and
-Mario García Valdez\inst{1} \and
-Juan J. Merelo Guervós\inst{2}}
-%
-\authorrunning{Felix-Saul et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{Department of Graduate Studies, Tijuana Institute of Technology, Tijuana, Mexico \and
-Department of Computer Architecture and Technology, Universidad de Granada, Granada, Spain}
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-%The abstract should briefly summarize the contents of the paper in 150--250 words.
+\maketitle
 
-Several bio-inspired algorithms use population evolution as analogies of
-nature. In this paper, we present an algorithm inspired by the biological
+\abstract*{Several bio-inspired algorithms use population evolution as
+analogies of nature. In this paper, we present an algorithm inspired by the
+biological Life-Cycle of animal species, which consists of several stages:
+birth, growth, reproduction, and death. As in nature, we intend to execute all
+these stages in parallel and asynchronously on a population that evolves
+constantly. From the ground up, we designed the algorithm as a cloud-native
+solution using the cloud available resources to divide the processing workload
+among several computers or running the algorithm as a cloud service. The
+algorithm works concurrently and asynchronously on a constantly evolving
+population, using different computers (or containers) independently,
+eliminating waiting times between processes. This algorithm seeks to imitate
+the natural life cycle, where new individuals are born at any moment and mature
+over time, where they age and suffer mutations throughout their lives. In
+reproduction, couples match by mutual attraction, where they may have
+offspring. Death can happen to everyone: from a newborn to an aged adult, where
+the individual's fitness will impact their longevity. As a proof-of-concept, we
+implemented the algorithm with Docker containers by solving the OneMax problem
+comparing it with a basic (sequential) GA algorithm, where it showed favorable
+and promising results.}
+
+\abstract{Several bio-inspired algorithms use population evolution as analogies
+of nature. In this paper, we present an algorithm inspired by the biological
 Life-Cycle of animal species, which consists of several stages: birth, growth,
@@
 Docker containers by solving the OneMax problem comparing it with a basic
-(sequential) GA algorithm, where it showed favorable and promising results.
-
-\keywords{Distributed Bioinspired Algorithms  \and Genetic Algorithms \and Cloud Computing.}
-\end{abstract}
+(sequential) GA algorithm, where it showed favorable and promising results.}
 
 \section{Introduction}
+\label{sec:1}
 
@@
 \label{proposal_section}
+% Always give a unique label
+% and use \ref{<label>} for cross-references
+% and \cite{<label>} for bibliographic references
+% use \sectionmark{}
+% to alter or adjust the section heading in the running head
 
@@
 
-Experiment 1: The goal of our first OneMax experiment was to make sure our
+\subsubsection{Experiment 1}
+The goal of our first OneMax experiment was to make sure our
 Life-Cycle algorithm worked as expected, converging on the solution. For this
@@
 
-Experiment 2: The goal of our second experiment was to confirm the Life-Cycle
+\subsubsection{Experiment 2}
+The goal of our second experiment was to confirm the Life-Cycle
 algorithm continued working as expected, converging on the solution. For this
@@
 
-Experiment 3: The goal of our third experiment was to follow and study the
+\subsubsection{Experiment 3}
+The goal of our third experiment was to follow and study the
 behavior of the Life-Cycle algorithm that continued converging on the solution.
@@
 
-Experiment 4: The goal of our fourth and last experiment was to follow and
+\subsubsection{Experiment 4}
+The goal of our fourth and last experiment was to follow and
 study the behavior of the Life-Cycle algorithm that continued converging on the
@@
     \end{figure}
-
-% Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.
 
@@
 
-\section*{Acknowledgments}
+\begin{acknowledgement}
+    This paper has been supported in part by projects DeepBio (TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
+\end{acknowledgement}
 
-This paper has been supported in part by projects DeepBio
-(TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
-%
-%
-%
-
-% Introducción 
-% Contexto: Los algoritmos bioinsirados se utilzan para resolver 
-% problemas complejos, pero en ocasiones se requiere de poder
-% computo.
-% Problemas: La mayoría de los algoritmos bio inspiarados
-% no están diseñandos con perspectiva distribuida, paralela y asíncrona. 
-% De que hay arquitecturas que tratan esta problematica. 
-% Propuesta. 
-% Descripción de las secciones del paper.
-
-% Estado del Arte 
-% PSO distribuido, GAs, etc.
-
-% Propuesta
-%
-
-% Experimental 
-% Setup 
-% OneMax
-% Results
-
-% Conclusiones
-
-%
 % ---- Bibliography ----
-%
 % BibTeX users should specify bibliography style 'splncs04'.
@@
 \bibliography{bib/bibliografia.bib}
-%
+
 \end{document}

### 2021-09-30 paper.tex
Final Updates
Missing abstract keywords
Final Updates
Image Labels update

@@
 
+%\keywords{Distributed Bioinspired Algorithms \and Genetic Algorithms \and Cloud Computing.}
+
 \section{Introduction}
@@
 propose a cloud-native optimization architecture that features population-based
-algorithms. They present ideas such as those mentioned in Figure~\ref{fig1},
+algorithms. They present ideas such as those mentioned in Figure~\ref{fig.background},
 which planted the seed of thought of our current paper.
@@
     \includegraphics[width=80mm]{img/fig1_background.pdf}
-    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig1}
+    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig.background}
     \end{figure}
@@
 newborn to an aged adult, where the individual's fitness will impact their
-longevity. The general model concept is shown in Figure~\ref{fig2}. The general
-flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig4}.
+longevity. The general model concept is shown in Figure~\ref{fig.proposal}. The general
+flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig.flowchart}.
 
@@
     \includegraphics[width=70mm]{img/fig2_proposal.pdf}
-    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig2}
+    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig.proposal}
+    \end{figure}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
+    \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
     \end{figure}
@@
     \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
-    \caption{Newton's Law of Universal Gravitation.} \label{fig3}
+    \caption{Newton's Law of Universal Gravitation.} \label{fig.newtonslaw}
     \end{figure}
@@
 
-\begin{figure}
-    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
-    \caption{Life-Cycle algorithm general flowchart.} \label{fig4}
-    \end{figure}
-
 \section{Experiments}
@@
     \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
-    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig5}
+    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig.processes_containers}
     \end{figure}
@@
 processes, up to the minimum number required to obtain good results.
-Figure~\ref{fig5} shows a comparison of only two alternatives for the
+Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the
 implementation of the algorithm. Our experimentation started with a
 configuration of ten processes and ended in five, shown on the left and right
-sides of Fig.~\ref{fig5}, respectively.
+sides of Fig.~\ref{fig.processes_containers}, respectively.
 

### 2021-09-30 paper.tex
Final Updates
Tables and figures label replacement

@@
 introduce our algorithm inspired by the Life-Cycle of animal species in
-section~\ref{proposal_section}, followed by our experimental configuration and
-results in section~\ref{experiments_section}, we analyze and describe some of
-our research findings in section~\ref{discussion_section}, and we finalize by
+section~\ref{section.proposal}, followed by our experimental configuration and
+results in section~\ref{section.experiments}, we analyze and describe some of
+our research findings in section~\ref{section.discussion}, and we finalize by
 presenting some inferences based on our experiments' results in
-section~\ref{conclusions_section}.
+section~\ref{section.conclusions}.
 
 \section{Proposal}
-\label{proposal_section}
+\label{section.proposal}
 % Always give a unique label
@@
 \section{Experiments}
-\label{experiments_section}
+\label{section.experiments}
 
@@
 the solutions in a similar number of evaluations and execution time.
-Table~\ref{tab1} shows the OneMax initial configuration for DEAP and Life-Cycle
+Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle
 experiment.
@@
     \centering        
-    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab1}
+    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab.configuration}
     \begin{tabular}{|l|l|l|}
@@
 
-\subsubsection{Experiment 1}
-The goal of our first OneMax experiment was to make sure our
-Life-Cycle algorithm worked as expected, converging on the solution. For this
-experiment, we intentionally used delays (on the tenth of a second magnitude)
-to follow the Life-Cycle algorithm behavior on the console output. For this
-experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
-processes (on containers) where we show the summarized results in Table~\ref{tab2}, and
-Figure~\ref{fig6} shows their Box and Whisker chart.
+\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
+make sure our Life-Cycle algorithm worked as expected, converging on the
+solution. For this experiment, we intentionally used delays (on the tenth of a
+second magnitude) to follow the Life-Cycle algorithm behavior on the console
+output. For this experiment, we compared the DEAP algorithm versus the
+Life-Cycle using ten processes (on containers) where we show the summarized
+results in Table~\ref{tab.experiment1}, and Figure~\ref{fig.experiment1} shows
+their Box and Whisker chart.
 
@@
     \centering        
-    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab2}
+    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab.experiment1}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig6}
+    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
     \end{figure}
 
-\subsubsection{Experiment 2}
-The goal of our second experiment was to confirm the Life-Cycle
-algorithm continued working as expected, converging on the solution. For this
-experiment, we reduced the time used on delays (now on the thousands of a
-second magnitude) to follow the Life-Cycle algorithm behavior. For this
-experiment, we only used tournament selection for the reproduction, on the
-first configuration running the Life-Cycle on ten processes, versus the second
-configuration where we reduced the processes to the minimum basic 5. We show
-the summarized results in Table~\ref{tab3}, and Figure~\ref{fig7} shows their Box and Whisker
-chart.
+\subsubsection{Experiment 2} The goal of our second experiment was to confirm
+the Life-Cycle algorithm continued working as expected, converging on the
+solution. For this experiment, we reduced the time used on delays (now on the
+thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
+For this experiment, we only used tournament selection for the reproduction, on
+the first configuration running the Life-Cycle on ten processes, versus the
+second configuration where we reduced the processes to the minimum basic 5. We
+show the summarized results in Table~\ref{tab.experiment2}, and
+Figure~\ref{fig.experiment2} shows their Box and Whisker chart.
 
@@
     \centering        
-    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab3}
+    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab.experiment2}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
+    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig.experiment2}
     \end{figure}
 
-\subsubsection{Experiment 3}
-The goal of our third experiment was to follow and study the
-behavior of the Life-Cycle algorithm that continued converging on the solution.
-For this experiment, we remained using minimal delays (thousands of a second
-magnitude). For this experiment, we only used tournament selection for the
-reproduction, on the first configuration running the Life-Cycle on six
+\subsubsection{Experiment 3} The goal of our third experiment was to follow and
+study the behavior of the Life-Cycle algorithm that continued converging on the
+solution. For this experiment, we remained using minimal delays (thousands of a
+second magnitude). For this experiment, we only used tournament selection for
+the reproduction, on the first configuration running the Life-Cycle on six
 processes, two of whom was the Death process, versus the second configuration
 where we reduced the processes to the minimum (five) but increasing the (Death)
-goal approval range to 115. We show the summarized results in Table~\ref{tab4},
-and Figure~\ref{fig8} shows their Box and Whisker chart.
+goal approval range to 115. We show the summarized results in
+Table~\ref{tab.experiment3}, and Figure~\ref{fig.experiment3} shows their Box
+and Whisker chart.
 
@@
     \centering        
-    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab4}
+    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab.experiment3}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig8}
+    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig.experiment3}
     \end{figure}
 
-\subsubsection{Experiment 4}
-The goal of our fourth and last experiment was to follow and
-study the behavior of the Life-Cycle algorithm that continued converging on the
-solution. For this experiment, we remained using minimal delays (thousands of a
-second magnitude). For this experiment, we compared the OneMax DEAP
-implementation versus the Life-Cycle algorithm, only using tournament selection
-for the reproduction, with the Life-Cycle configuration running on the minimum
-(five) processes but increasing the (Death) goal approval range to 125. We show
-the summarized results in Table~\ref{tab5}, and Figure~\ref{fig9} shows their Box and Whisker
-chart.
+\subsubsection{Experiment 4} The goal of our fourth and last experiment was to
+follow and study the behavior of the Life-Cycle algorithm that continued
+converging on the solution. For this experiment, we remained using minimal
+delays (thousands of a second magnitude). For this experiment, we compared the
+OneMax DEAP implementation versus the Life-Cycle algorithm, only using
+tournament selection for the reproduction, with the Life-Cycle configuration
+running on the minimum (five) processes but increasing the (Death) goal
+approval range to 125. We show the summarized results in
+Table~\ref{tab.experiment4}, and Figure~\ref{fig.experiment4} shows their Box
+and Whisker chart.
 
@@
     \centering        
-    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab5}
+    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab.experiment4}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig9}
+    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig.experiment4}
     \end{figure}
@@
 \section{Discussion}
-\label{discussion_section}
+\label{section.discussion}
 
@@
 \section{Conclusions}
-\label{conclusions_section}
+\label{section.conclusions}
 

### 2021-10-03 paper.tex
Minor typo

@@
 
-This scheme allows for multiple parameter's fine tunning, granting us the
+This scheme allows for multiple parameter's fine tuning, granting us the
 freedom to experiment with different selection and reproduction strategies

### 2021-10-03 paper.tex
Some corrections here and there

@@
 \abstract*{Several bio-inspired algorithms use population evolution as
-analogies of nature. In this paper, we present an algorithm inspired by the
+analogies of Nature. In this paper, we present an algorithm inspired by the
 biological Life-Cycle of animal species, which consists of several stages:
 birth, growth, reproduction, and death. As in nature, we intend to execute all
+% single animals in animal species? Species follow a different lifecycle... - JJ
 these stages in parallel and asynchronously on a population that evolves
 constantly. From the ground up, we designed the algorithm as a cloud-native
-solution using the cloud available resources to divide the processing workload
+solution leveraging cloud  resources to divide the processing workload
 among several computers or running the algorithm as a cloud service. The
 algorithm works concurrently and asynchronously on a constantly evolving
-population, using different computers (or containers) independently,
+population, using different computing nodes (or containers) independently,
 eliminating waiting times between processes. This algorithm seeks to imitate
 the natural life cycle, where new individuals are born at any moment and mature
-over time, where they age and suffer mutations throughout their lives. In
-reproduction, couples match by mutual attraction, where they may have
+over time, where they age and suffer mutations throughout their lives.
+% Individuals don't suffer inheritable mutations. That would be a Lamarckian view of evolution - JJ
+In
+reproduction, couples match by mutual attraction, % But this is related to fitness - JJ
+and they may have
 offspring. Death can happen to everyone: from a newborn to an aged adult, where
@@
 \cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
-distinguishes us, is that our proposal presents an algorithm designed in its
+distinguishes this proposal is the introduction of  an algorithm designed in its
 entirety as a native solution in the cloud, fully distributed, where its
-processes are executed in parallel and asynchronously. This technique makes it
+processes are executed in parallel and interaction takes place asynchronously. This technique makes it
 easy to scale the computing power according to the complexity required by the
@@
 introduce our algorithm inspired by the Life-Cycle of animal species in
+% Please use capitalization consistently; I don't think this should go in Caps - JJ
 section~\ref{section.proposal}, followed by our experimental configuration and
@@
 mutations throughout their lives. In reproduction, couples match by mutual
-attraction, where they may have offspring. Death can happen to everyone: from a
+attraction, and they may have offspring. Death can happen to everyone: from a
 newborn to an aged adult, where the individual's fitness will impact their
@@
     \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
+% Several terms are introduced here that are not defined in the text, like "champion list" and "attraction" - JJ
     \end{figure}
@@
 The growth process will take an individual to assess whether it's ready to
-mature and undergo changes.
+mature and undergo changes. % Not learning?  JJ
 
@@
 attractive it is to its mating candidates. To be consistent with both ideas in
+% Er... not really. It depends on health, mainly - JJ
 our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
@@
 \end{itemize}
+
+% to be honest, I find this a bit far fetched. How do you define mass? is it related to fitness? - JJ
 
@@
     \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
+    \caption{Box and whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
+% You need to label axis y - JJ
   \end{figure}
